\documentclass[12pt]{article}
\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}

\section{Newton-Okounkov Bodies}

Let $X / k$ be a projective variety, with $k$ arbitrary (is not equipped with a valuation). We consider valuations $\nu : K(X)^\times \to \RR^d$ with $\RR^d$ taking the lexicographic order where $d = \dim{X}$. There is a valuation with full rank for $d$ the dimension meaning its image is a lattice. 
\bigskip\\
We use this valuation to measure the size of divisors. 

\begin{defn}
The \textit{Newton-Okounkov Body} of a divisor $D$ wrt $\nu$ is the set,
\[ \Delta_\nu(D) = \overline{ \bigcup_{n \ge 1} \{ \tfrac{1}{n} \nu(f) \mid f \in H^0(X, n D) \} } \subset \RR^d \]
\end{defn}

\newcommand{\Vol}{\mathrm{Vol}}

\begin{theorem}[Lazarsfeld-Mustata]
$\Vol(\Delta_\nu(D)) = \frac{1}{d!} \Vol(D) \cdot \Vol(\Im{\nu})$ where the volume of a divisor $D$ is $\Vol(D) = d! \deg{D^d}$ is given by intersection theory as is equal (by Riemann-Roch) to,
\[ \Vol(D) = \lim_{n \to \infty} \frac{h^0(X, nD)}{n^d} \]
\end{theorem}

\begin{rmk}
The usual setting is where we take $\nu$ to be a flag valuation. Consider a flag of subvarities,
\[ * = Y_0 \subsetneq Y_1 \subsetneq \cdots \subsetneq Y_{d-1} \subsetneq Y_d = X \]
where the valuation is defined by the order of vanishing of a function proceeding down the flag.  
\end{rmk}

\begin{rmk}
In dimension $2$ there is a formula for $\Delta_\nu(D)$ in terms of Zariski decomposition.
\end{rmk}

\begin{rmk}
$\Delta_\nu(D)$ only depends on the numerical class of $D$. 
\end{rmk}

Consider the variation of $\nu \mapsto \Delta_\nu(D)$. We construct a family $\nu_s$ for $s \ge 1$ depending on a curve $C$. Let $X = \P^2$ and $D$ a line. Then we write,
\[ \nu_s(f) = \nu_s(\sum_{i,j} a_{i,j} x^i t^j) := \min \{ i + s j \mid a_{i,j} \neq 0 \} \]
with weights $1$ and $s$. This is a rank $1$ valuation. We want a rank $2$ valuation to study the Okounkov body. Thus write,
\[ \nu_s := (\nu_s^1(f), D_+ \nu_0(f)(s)) \]
this is a rank $2$ valuation. 

\end{document}