\documentclass[12pt]{article}
\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}

\subsection{$K$-theory of the moduli space of genus zero curves}


\begin{defn}
$\M_{0,n}$ parametrizes genus zero curves with $n$ labeled distinct points (up to isomorphism fixing the marked points). 
\end{defn}

\begin{rmk}
We will always take $n \ge 3$ for stability reasons. Notice that $\M_{0,3} = *$ and $\M_{0,4} = \P^1 \setminus \{ 0, 1, \infty \}$. We see that $\M_{0,n}$ is noncompact. We will consider a nice compactification. 
\end{rmk}

\begin{defn}
$\overline{\M}_{0,n}$ parametrizes stable genus zero curves with $n$ marked points. This is a tree of $\P^1$ with at last $3$ nodes or marked points on each component. 
\end{defn}

\begin{example}
$\overline{\M}_{0,3} = *$ and $\overline{\M}_{0,4} =  \P^1$ and $\overline{\M}_{0,5}$ is the blowup of $\P^2$ at four general points. 
\end{example}

\begin{prop}
$\dim{\overline{\M}_{0,n}} = n - 3$ and $\M_{0,n} \subset \overline{\M_{0,n}}$ is a dense open. 
\end{prop}

\begin{rmk}
$\psi : \overline{\M}_{0,n+1} \to \overline{\M}_{0,n}$ forgetting points and contracting components if necessary induces a birational map then there are sections $s_i$ which induce divisors and we define the $\psi_i$ classes as the conormal bundles of these sections.
\end{rmk}

\begin{thm}[Kapranov]
The $\psi_i$ are base-point-free line bundle and defines a birational map,
\[ \overline{\M}_{0,n} \onto \P^{n-1} \]
where $\overline{\M}_{0,n}$ maps to 
\end{thm}

\begin{rmk}
For $S \subset [1, \dots, n-1]$ with $|S| \ge 3$ we can consider forgetfull maps,
\begin{center}
\begin{tikzcd}
\overline{\M}_{0,n} \arrow[rd] \arrow[d]
\\
\overline{\M}_{0,k} \arrow[r, "\psi"] & \P^{k-2}
\end{tikzcd}
\end{center}
therefore we have,
\[ \overline{\M}_{0,n} \embed \prod_{\substack{S \subset [n-1] \\ |S| \ge 3}} \P^{|S| - 2} \]
Then we let $X_s = C_i(f_* \psi_n)$ 
\end{rmk}



\end{document}
