\documentclass[12pt]{article}
\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}
\section{Higher Dimensional Fano Varieties}

Aim: identify a class of fano varitieties that can be described mostly combinatorially and in each dimension there is a sizable amount of these Fanos. We work over $\CC$.

\begin{defn}
Two pairs $(X, B)$ and $(X', B')$ are ``crepant birationally equivalent'' if there is a common resolution $p : Y \to X$ and $q : Y \to X'$ such that $p^* (K_X + B) = q^* (K_{X'} + B')$ as divisors. We write $X \simeq_{\text{crbir}} X"$.
\end{defn}


\begin{defn}
A variety $X$ is \textit{rational} if $X$ is birationally equivalent to $\P^n$. A normal (irreducible) variety $X$ is \textit{toric} if it has an open $U \cong \Gm^n$ and the action extends to $X$. 
\end{defn}

A notion that interpolates between the two is:

\begin{defn}
A variety is \textit{log-rational} if there exists effective $B$ with $(X, B) \simeq_{\text{crbir}} (\P^n, H_0 + \cdots + H_n)$.
\end{defn}

\begin{defn}
A variety $X$ is \textit{of cluster type} if there exists a crepant birational equivalence $\varphi : (\P^n, H_0 + \cdots + H_n) \rat (X, B)$ with $\Exc{\varphi} \cap \Gm^n$ has codimension $\ge 2$ in $\Gm^n$ for some effective $B$. 
\end{defn}

\begin{theorem}[Enwright-Figuerioa-Moraga, 24] 
Let $X$ be a $\Q$-factorial Fano variety. Let $(X, B)$ be of cluster type. Then $\struct{}(X \sm B)$ is a cluster algebra. 
\end{theorem}

\begin{defn}
An integral domain (commutative ring) $A$ is a \textit{cluster algebra} if $\Spec{R}$ is divisorially covered\footnote{Meaning it is a cover away from codimension $2$} by copies of $\Gm^n$ and the transition functions preserve the volume form:
\[ \frac{\d{x_1} \wedge \cdots \wedge \d{x_n}}{x_1 \cdots x_n} \]
\end{defn}

\begin{theorem}
A general smooth del Pezzo surface is of cluster type. 
\end{theorem}

\begin{proof}
$X$ is the blowup of $\P^2$ at $k \le 8$ points. We need to find an anticanonical nodal divisor $B$ and this will be our candidate. Therefore we need to put a nodal cubic in $\P^2$ through these points. Then $(X, B) \simeq_{\text{crbir}} (\P^2, C_3)$. Then we apply Cremona transformations of $(\P^2, C_3)$. This gives log rational but we messed up the exceptionals too much. We need to be more careful to get cluster type. We use explicit blowups and the fact that all toric varities are crepant birational in a way that is an isomorphism on the torus. We needed to start with a node because the dimension of the minimal lc centers of a log-CY pair is a crepant birational invariant. 
\end{proof}

Idea: a deformation class of cluster type Fano varieties can be encoded in a polytope and a quiver. 

Q: let $(X, B)$ be a log Calabi-Yau pair $(K_X B \sim_{\Q} 0$ with $(X, B)$ log canonical. Is $(X, B) \simeq_{\text{crbir}} (\P^n, H_0 + \cdots + H_n)$. 

\begin{defn}
The dual complex of a log CY-pair $(X,B)$ denote by $D(X,B)$ is a CW complex whose points are in correspondence with prime divisors of $B$ and $k$-cells correspond to irreducible components of intersections of $k+1$ prime divisors of $B$. 
\end{defn}

\begin{rmk}
If $(X, B) \simeq_{\text{crbir}} (\P^n, H_0 + \cdots + H_n)$ then $K_X + B \sim 0$. If $(X, B) \simeq_{\text{crbir}} (X', B')$ with $(X,B)$ and $(X', B')$ log CY pairs of index one then $D(X, B) \simeq_{\text{PL}} D(X', B')$. Therefore, if $(X, B)$ is log rational, then $D(X,B) \simeq S^{n-1}$ and $n = \dim{X}$. 
\end{rmk}

Conjecture(Shokurov): let $(X, B)$ be a log CY-pair. If $(X, B) \simeq_{\text{PL}} S^{n-1}$ where $n = \dim{X}$ then $(X,B)$ is log rational (has a toric model). 

\begin{theorem}
There exists a birationally superrigid 3-fold $X$ and a boundary $B$ for which $D(X, B) \simeq_{\text{PL}} S^2$. 
\end{theorem}

This gives a counterexample since $\P^n$ is not birationally rigid. 

\begin{theorem}[Gross-Hacking-Keel]
The conjecture is true in dimension $2$.
\end{theorem}

Conjecture: let $(X,B)$ be a log-CY pair of dimension $n$. Assume $D(X, B) \simeq_{\text{PL}} S^{n-1}$ and every dlt strata of $(X,B)$ is rational then $(X,B)$ is log rational. 

\begin{theorem}[Loginov-M-Vasilkov]
Let $X$ be a general rational smooth Fano 3-fold then $X$ is log rational. 
\end{theorem}

\begin{rmk}
Mori-Mukai: there are 105 families of smooth Fano 3-folds and 88 of these families have rational general element.
\end{rmk}

\begin{theorem}[Ducat, 23]
Let $(\P^3, B)$ be a log CY 3-fold with a 0-strata then $(\P^3, B)$ is log rational. 
\end{theorem}

\begin{theorem}[Loginov-M]
Ducat's theorem also holds if we replace $\P^3$ with a quadric 3-fold. 
\end{theorem}

\section{Motivation}

\begin{defn}
A \textit{boundary polarized CY pair} $(X, D)$ is a pair so that
\begin{enumerate}
\item $(X, D)$ has semi-log canonical singularities
\item $K_X + D \sim_{\Q} 0$ but we do not assume that $K_X$ or $D$ are $\Q$-Cartier. Then the smallest $N$ so that $N(K_X + D) \sim 0$ is called the \textit{index}
\item $D$ is ample $\Q$-Cartier divisor 
\end{enumerate}
\end{defn}

\begin{rmk}
$X$ is an slc Fano varitey. 
\end{rmk}

\begin{example}
\begin{enumerate}
\item Consider $(\P^2, \frac{3}{d} C_d)$ with a degree $d$ curve
\item $(\P^n, \frac{n+1}{d} H_d)$ with a degree $d$ hypersurface
\item $(Y,L)$ is an polarized honest CY (meaning $K_Y \sim \Q$) then
\[ X = \ol{C}(Y,L) = \Proj{ \bigoplus_{i,j \ge 0} H^0(Y, \floor{ i L }) t^j \]
and $(X, H_{\infty})$ is a bpCY
\item hyperelliptic K3s with a double cover:
\[ (X, \tfrac{1}{2} B) \quad B \in | -2 K_X | \]
where $X$ is a del Pezzo surface. A double cover branched along $B$ has $Y$ a K3-surface.
\end{enumerate}
\end{example}

\subsection{General Type Case}

Let $(X, \Delta)$ be log general type i.e. $K_X + \Delta$ is big. Then MMP gives $(X, \Delta) \rat (X^\can, \Delta^\can)$ so $K_{X^\can} + \Delta^{\can}$ is ample. Then KSBA moduli space parametrizes the canonical models. There is a stack
\[ \M^{KSBA}_{d, v, I} \]
where $I = (a_1, \dots, a_r)$ is a list of the coefficients:
\[ \Delta = a_1 D_1 + \cdots + a_r D_r \]
and $v$ is the volume of $K_X + \Delta$ and $d = \dim{X}$. This stack satisfies
\begin{enumerate}
\item it is a proper DM-stack
\item has a projective coarse space
\item have to deal with slc singularities in order for it to be proper.
\end{enumerate} 

\subsection{Log Fano Case}

We start with a pair $(X, \Delta)$ where $-(K_X + \Delta)$ is ample. We ask: is $(X, \Delta)$ a $K$-semistable pair? If so, we get a good moduli space:
\[ \M^{K}_{d, v, I} \]
where $I$ is the coefficent set, $v$ is the volume, and $d = \dim{X}$ satisfying
\begin{enumerate}
\item we only need klt singularities (so no need for non-normal slc singularities)
\item Artin stack with a proper good moduli space 
\item the good moduli space is projective 
\item however, it is hard to check if $(X, \Delta)$ is $K$-semistable
\end{enumerate}
Note that $K$-semistability is an open condition in families. 

\subsection{bpCY interpolates between these two cases}

Consider $(X, D)$ a bpCY that is klt. Being klt is preserved by pertubations in the coefficients. Therefore, we can consider $(X, (1 \pm \epsilon) D)$ which is also klt. We have $K_X + (1 \pm \epsilon) D \sim_{\Q} \pm \epsilon D$ and $D$ is ample so for $(+)$ we get a KSBA stable pair and for $(-)$ we get a klt log Fano. Therefore,
\[ \M^K_{-\epsilon} \subset \M^{CY} \supset \M^{KSBA}_{+\epsilon} \]
Since both sides have projective moduli spaces we want a moduli space for $\M^{CY}$ completing the diagram:
\begin{center}
\begin{tikzcd}
\M^K_{-\epsilon} \arrow[r, hook] \arrow[d] & \M^{CY} \arrow[from=l, hook] & \M^{KSBA} \arrow[d]
\\
M^K \arrow[r] & M^{CY} \arrow[from=l] & M^{KSBA}
\end{tikzcd}
\end{center}
Dream: $M^{CY}$ is the common ample model of $\lambda_{\text{Hodge}}$ pulling back. 


For KSBS whenever we lower the coefficients we get an open inclusion of the Moduli space (raising the coeffifiencts for K-moduli) but we only get a roof for the coarse spaces. 

\begin{theorem}[Alper, Halpern-Leistner, etc]
If $\X$ is a finite type stack with affine diagonal then $\X$ admits a GMS $\pi : \X \to X$ if and only if $\X$ is $\Theta$-reductive and $S$-complete. Moreover $X$ is proper iff $\X$ satisfies the existence part of the valuative criterion.
\end{theorem}

\begin{theorem}[WILDBAB]
There exists a locally finite type algebraic stack $\M^{CY}$ parametrizing bpCY. It satisfies
\begin{enumerate}
\item $\Theta$-reductivity
\item $S$-completeness
\item affine diagonal
\item existence part of valuative criterion.
\end{enumerate}
\end{theorem}

\begin{rmk}
$S$-equivalence is generated by taking a map from $\Theta := [\A^1 / \Gm]$ and taking the images of $0,1$ to be $S$-equivalent. We say that $\X$ is $S$-complete if the functor of $S$-equivalence classes is separated. What it means is limits in $\X$ are unique up to $S$-equivalence. Then $X$ will be ``quotient'' by $S$-equivalence. 
\end{rmk}

Problem: $\M^{CY}$ is NOT quasi-compact. However, the above properties say that:

\begin{cor}
For any closed $\Z \subset \M^{CY}$ that is quasi-comapct there is a good moduli space. 
\end{cor}

\begin{example}
$(\P^2, \frac{3}{3} C_3)$ deformation to the normal cone to get a cone over an elliptic curve. Then we degenerate the elliptic curve to an $n$-gon of $\P^1$ and taking the cone gives larger and larger degenerations with increasing automorphism group. 
\end{example}

\begin{theorem}
Let $\cP_d = \ol{\{ (\P^2, \tfrac{3}{d} C_d) \}}^{bpCY} \subset \M^{CY}$ then 
\begin{enumerate}
\item there exists an asymtotically good moduli space $\cP^{CY}_d \to P_d$ 
\item $\cP^K_d \subset \cP^{CY}_d \supset \cP^H_d$ compatible with the moduli spaces
\item and $\lambda_{\text{Hodge}$ is ample on $P_d$. 
\end{enumerate}
\end{theorem}

\begin{example}get $C(E)$
$P_6^{CY}$ is the Baily-Borell compactification of K3 surfaces.
\end{example}

\end{document}
