\documentclass[12pt]{article}
\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}

\section{Pre-talk question.}



Let $Y_1(N) / \FF_p$ with $(p,N) = 1$ be the level $N$ modular curve which is the moduli space of elliptic curves with level structure. 
\bigskip\\
Recall that an elliptic curve $E / \FF_p$ is \underline{ordinary} if of the equivalent properties hold,
\begin{enumerate}
\item $E[p](\overline{\FF_p}) \cong \Z / p \Z$ 
\item $E[p^n](\overline{\FF_p}) \cong \Z / p^n \Z$
\item $E_{\overline{\FF_p}}[p^\infty] \cong \Q_p/\Z_[ \oplus \mu_{p^\infty}$
\end{enumerate}
Otherwise $E$ is supersingular. The locus $Y_1(N)^\ord \subset Y_1(N)$ is open. We cannot expect,
\[ X = \E[p^\infty]/Y_1(N)^\ord \]
to be \etale locally isomorphic to $\Q_p/\Z_p \oplus \mu_{p^\infty}$. However, there is an exact sequence,
\begin{center}
\begin{tikzcd}
0 \arrow[r] & X^1 \arrow[r] & X \arrow[r] & X^0 \arrow[r] & 0
\end{tikzcd}
\end{center}
where $X^1$ is multiplicative and $X^0$ is \etale (SOMTHING?)
\bigskip\\
We define the Igusa variety,
\[ IG^\ord \]
as the moduli space of isomorphisms $X^0 \iso \Q_p / \Z_\p$ and $X^1 \iso \mu_{p^\infty}$. Them
\[ IG^\ord = \varprojlim IG^\ord_p \]
Then $IG^\ord$ is a $\underline{\Z_p}^\times \times \underline{\Z_p}^\times$ pro-\etale torsor.

\begin{rmk}
Why is this useful? We can lift $Y_1(N)^\ord$ to a formal scheme over $\Z_p$ then $IG^\ord$ lifts to a torsor over the formal scheme $\mathcal{IG}^\ord$. Sections of this torsor are used to define $p$-adic modular forms. Indeed, $p$-adic modular forms (a la Katz or Hidas) are exactly sections of the lifted Igusa variety. 
\end{rmk}

\begin{thm}[Igusa]
$\pi_0(IG^\ord) \cong \Z_p^\times$ 
equivariantly for the $\Z_p^\times \times \Z_p^\times$ action via $(a,b) \mapsto ab^{-1}$.
\end{thm}

Let $\cA_{g,N}$ be the moduli space of principally polarized abeilain varieties and let $\Sigma$ be a fixed polarized $p$-divisoble group. Then $C_\Sigma \subset \cA_{g,N}$ consisting of those $\FF_p$-points $A$ such that $A[p^\infty] \cong C_\Sigma$ compatibly wit hthe polarisations up to a $\Z_p^\times$-scalar.

\begin{thm}[Oort]
$C_\Sigma$ is locally closed, smooth, equidimensional and there is an Igusa variety $IG_\Sigma \to C_\Sigma$ and this is an $\Aut{\Sigma}$-torsor.
\end{thm}

\begin{thm}[Chai-Oort]
If $\Sigma$ is not supersingular, then $C_\Sigma$ is connected and $\pi_0(IG_\Sigma) \cong \Z_p^\times$.
\end{thm}

Let $(G, X)$ be a Shimura datum of Hodge type $\sigma$ and $p > 2$ a prime where $G_{\Q_p}$ is unramified $U^p \subset G(\A^p_f)$ a compact open $U_p \subset G(\Q_p)$ hyperspecial. We let,
\[ \Sh_f / \overline{\FF_p} \]
be the special fiver of the canonical integral model (exists by Kisin). Then we also get,
\[ C_\Sigma \subset \Sh_G \]
locally closed, smooth (Kisin) and Igusa varieties,
\[ IG_\Sigma \to C_\Sigma \]
Then $IG_\Sigma$ is a torsor for some profinite group.

\newcommand{\der}{\mathrm{der}}

\begin{theorem}
Assume $G^\der$ is simply connected, $G^\ab$ is $\Q$-simple, and that $p \ndivides W_G$ where $W_G$ is the Weil group. If $C_\Sigma$ is not contained in the basis locus,
\[ \pi_0(IG_\Sigma) \cong \pi_0(\Sh_G) \times G^\ab(\Z_p) \]
\end{theorem}

\begin{rmk}
If $C_\Sigma \subset \Sh_{G_U}$ base $U$ then $IG_{\Sigma}$ is 0-dimensional. Some results obtained by Knet-Shing using different methods such as asymtotic point counts.
\end{rmk}

\begin{rmk}
$IG_{\Sigma} \to C_\Sigma$ is a profinite $H_\Sigma$-torsor so 
\[ \pi_0(C_\Sigma) = \pi_0(IG_\Sigma)/H_\Sigma = \pi_0(\Sh_{G_\sigma}) \times \frac{G^\ab(\Z_p)}{H_\Sigma} \]
Since the second term is not always trivial this gives counter examples to the discrete Hecke orbit conjecture of Chai-Oort.
\end{rmk}

\begin{rmk}
Using results of Zhou-Zhu (proof of the Chen-Zhu conjecture), we determine irreducible components of Newton strata using the product formula.
\end{rmk}


\end{document}
