\documentclass[12pt]{article}
\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}

\subsection{Rational Connectedness}

\begin{defn}
A variety $X$ is \textit{rationally connected} if there is a rational curve connecting a general pair of points on $X$.
\end{defn}

\begin{defn}
A variety $X$ is \textit{rationally chain connected} if there is a chain of $\P^1$ though every general pair of rational points.
\end{defn}

There are two issues in formalizing,
\begin{enumerate}
\item If $k$ is finite then there can be rational curves though all rational points but not closed points
\item If characteristic of $k$ is positive, rational connectedness can come from some inseparable family.
\end{enumerate}


\begin{defn}
$X$ is \textit{rationally connected} if there is a family $U$ of rational curves on $X$ meaning a map $u : U \times \P^1 \to X$ such that $u^{(2)} : U \times \P^1 \times \P^1 \to X \times X$ is dominant. We say that $X$ is \textit{separably rationally connected} if $u : U \times \P^1 \to X$ can be chosen with $u^{(2)}$ is smooth.
\end{defn}

\begin{rmk}
If $\mathrm{char}(k) = 0$ and $X$ is smooth then the following are equivalent,
\begin{enumerate}
\item $X$ is rationally chain connected
\item $X$ is rationally connected
\item $X$ is separably rationally connected.
\end{enumerate}
\end{rmk}

\begin{rmk}
However, in positive characteristic, SRC is the ``nicest'' notion.
\end{rmk}

\begin{thm}[de Jong - Starr]
If $\pi : X \to B$ is proper, flat with normal SRC fibers and $B$ is a curve then $\pi$ admits a section.
\end{thm}

\begin{thm}[Tian-Zong]
Chow groups of $1$-cycles on $X$ SRC are generated by rationa lcurves.
\end{thm}

\begin{thm}
If $X$ is smooth and SRC then $H^1(X, \struct{X}) = 0$. 
\end{thm}

\subsection{Fano Varieties}

\begin{defn}
A normal $\Q$-Gorenstein variety $X$ is \textit{Fano} if $-K_X$ is ample.
\end{defn}

\begin{example}
Some Fano varieties,
\begin{enumerate}
\item $\P^n$
\item $\mathrm{Gr}(k,n)$
\item $X = G / P$.
\item low degree complete intersection in the above.
\end{enumerate}
\end{example}

Fano varieties have a lot of rational curves. This uses Mori bend and break. 

\begin{prop}
If $X$ is a smooth Fano variety, then $X$ is rationally chain-connected.
\end{prop}

\begin{rmk}
Question: given $X$ smooth Fano, is $X$ SRC in positive characteristic.
\end{rmk}

\begin{rmk}
The smoothness condition is essential here. Kollar gives an example of a singular Fano variety that is not SRC. 
\end{rmk}

\begin{example}
Some more examples,
\begin{enumerate}
\item $\P^n$ is SRC by lines
\item $X = G/P$ homogeneous with $P$ reduced is also SRC
\item If $P$ is not reduces then $G/P$ is more mysterious but not provably not SRC (yet)
\end{enumerate}
\end{example}

\begin{thm}[Chen-Zhu, Tian]
A general Fano complete intersection in $\P^n$ is SRC. 
\end{thm}

\begin{proof}
Tian notes that these varieties are separably uniruled and shows that if they aren't SRC, their tangent bundle is unstable but in general these tangent bundle is stable.
\bigskip\\
Chen-Zhu treat this as a problem in log geometry. 
\end{proof}

\begin{rmk}
Don't say much about how the rational curves involved.
\end{rmk}

\subsection{Free Curves and Very Free Curves}

\begin{defn}
Let $\iota : \P^1 \to X$ be an immersion into the smooth locus on $X$. Let $C = \iota(\P^1)$. We say that,
\begin{enumerate}
\item \item $C$ is \textit{free} if $\iota^* \T_X$ is globally generated
\item $C$ is \textit{very free} if $\iota^* \T_X$ is ample.
\end{enumerate}
\end{defn}

\begin{rmk}
By the structure of bundles on $\P^1$,
\[ \iota^* \T_X = \bigoplus_{i} \struct{\P^1}(e_i) \]
Then $C$ is free iff every $e_i \ge 0$ and $C$ is very free iff every $e_i \ge 1$.
\end{rmk}

\begin{theorem}
If $X$ is smooth then,
\begin{enumerate}
\item $X$ is SRC iff it has a very free curve
\item $X$ is separably uniruled iff it has a free curve.
\end{enumerate}
\end{theorem}

\begin{thm}[Costum - S]
Let $X = \mathrm{Gr}(k,n)$ and let $Y$ be a general Fano complete intersection in $X$ of hypersurfaces $Y_i$, each of class $d_i H$ where $H$ is the ample class with $d_i \ge 3$. Then $Y$ is SRC, and has a very free curve of the ``lowest possible degree''
\end{thm}

\begin{thm}
Let $X$ be a projective variety, $H$ very ample, giving an embedding $X \embed \P^n$, ideal sheaf $\theta_{X|\P^n}(k H)$ is glovally generated. 
\bigskip\\
If $C$ is a very free curve on $X^{\text{smooth}}$ thet is a rationa lnormal curve in $\P^n$, and $Y_1, \dots, Y_\ell$ general hypersurfaces with $Y_i$ of class $d_i H$ and $d_i \ge \max \{ k, \xi \}$ each containing $C$ and,
\[ C \cdot (-K_X - d_1 - \dots - d_i) \ge \dim{X} - c + 1 \]
the n $C$ stays very free in $Y = Y_1 \cap \cdot \cap Y_i \cap X$ (an irreducible variety smooth along $C$). So $Y$ ands deformations are RSR.
\end{thm}

\begin{rmk}
In higher pricard rank, a similar result does hold but it's more complicated. To apply this result:
\begin{enumerate}
\item Need a very ample class $H$ on $X$ such that $X \subset \P^n$ is cut out out by hypersurfaces of low degree
\item Need a rational normal curve in $\P^n$ that is also very free on $X$.
\end{enumerate}
\end{rmk}

\begin{rmk}
(a) is pretty straightforward because we can embed as an intersection of quadrics
\bigskip\\
(b) is harder. For the grassmanian, $\mathrm{Gr}(k,n)$ use the map $\P^1 \to \mathrm{Gr}(k,n)$ given by an explicit matrix. You can do this on flag varieties, products, some weighted projective spaces etc.
\end{rmk}

\begin{rmk}
Is there a similar way of finding rational curves on more general homogeneous varieties?
\end{rmk}

\end{document}
