\documentclass[12pt]{article}
\usepackage{import}
\import{./}{AlgGeoCommands}

\begin{document}

\section{Coherent Sheaves}

\section{Analytic Spaces}

(DO DEFINITION!!!)

\begin{defn}
An \textit{affine analytic space} $X$ is 
\end{defn}

\begin{defn}
An \textit{analytic space} $X$ is a locally ringed space $(X, \struct{X})$ which is locally isomorphic to affine analytic spaces.
\end{defn}

\begin{theorem}
Let $X$ be an analytic space. Then $\struct{X}$ is coherent. 
\end{theorem}

\section{Analytification}

\begin{defn}
Analytification is the unique functor $(-)^\an : \mathbf{Var}_k \to \mathbf{AnSpa}_k$ along with a map $a : X^\an \to X$ of locally ringed spaces satisfying:
(DO THIS!!!!)
\end{defn}

\begin{lemma}
The canonical map $a : X^\an \to X$ of locally ringed spaces is:
\begin{enumerate}
\item flat
\item open
\item 
\end{enumerate}
\end{lemma}

\begin{defn}
Let $\F$ be a $\struct{X}$-module on a $k$-variety $X$. Then the analytification of $\F$ is the $\struct{X}^\an$-module $\F^\an = a^* \F$ on $X^\an$ where $a$ is the canonical map $a : X^\an \to X$. 
\end{defn}

\begin{prop}
If $\F$ is a coherent $\struct{X}$-module. Then $\F^\an$ is a coherent $\struct{X}^\an$-module.
\end{prop}

\section{The Main Theorems}

\subsection{The Equivalence of Cohomology}

\begin{theorem}
Let $X$ be a projective variety over $k$ and $\F$ be a coherent $\struct{X}$-module. Then the natural map,
\[ H^q(X, \F) \xrightarrow{\sim} H^q(X^\an, \F^\an) \]
is an isomorphism. 
\end{theorem}

\subsection{The Equivalence of Morphisms}

\begin{lemma}
Let $M, N$ be $A$-modules and $B$ an $A$-algebra. Then the natural map,
\[ \Hom{A}{M}{N} \otimes_A B \to \Hom{A}{M}{N \otimes_A B} = \Hom{B}{M \otimes_A B}{N \otimes_A B} \]
is an isomorphism when $M$ is finite projective or $B$ is $A$-flat. 
\end{lemma}

\begin{proof}
(DO THIS!!!!)
\end{proof}

\begin{lemma}
Let $(X, \struct{X})$ be a ringed space and $\F, \G$ be $\struct{X}$-modules. Then the natural map,
\[ \shHom{\struct{X}}{\F}{\G}_x \to \Hom{\stalk{X}{x}}{\F_x}{\G_x} \]
is an isomorphism when $\F$ is finitely-presented.
\end{lemma}

\begin{proof}
 Gortz, T. Wedhorn: Algebraic Geometry 1, Chapter 7, Prop: 7.27
 \\
 EGA I, chapter 0, 6.7.6 
\end{proof}

\begin{lemma}
Let $f : (X, \struct{X}) \to (Y, \struct{Y})$ be a morphism of ringed spaces and $\F, \G$ be $\struct{Y}$-modules. Then the natural map,
\[ f^* \shHom{\struct{Y}}{\F}{\G} \to \shHom{\struct{X}}{f^* \F}{f^* \G} \]
is an isomorphism when $\F$ is finite locally free or $\F$ is finitely presented and $f : X \to Y$ is flat.
\end{lemma}

\begin{proof}

\end{proof}

\begin{theorem}[GAGA II]
Let $X$ be a (projective?) variety over $k$ (hypotheses?). Then, for coherent $\struct{X}$-modules $\F, \G$ the natural map,
\[ \shHom{\struct{X}}{\F}{\G}^\an \xrightarrow{\sim} \shHom{\struct{X}^\an}{\F^\an}{\G^\an} \]
is an isomorphism.
\end{theorem}

\begin{proof}
This is simply an application of the previous lemma to the map $f : X^\an \to X$ of locally ringed spaces which is flat. Since $\F$ and $\G$ are coherent they are finitely presented.
\end{proof}

\begin{corollary}
Let $X$ be a projective variety over $k$ and let $\F, \G$ be coherent $\struct{X}$-modules. Then,
\[ \Hom{\struct{X}^\an}{\F^\an}{\G^\an} = \Hom{\struct{X}}{\F}{\G} \]
\end{corollary}

\begin{proof}
Use GAGA II to give $\shHom{\struct{X}}{\F}{\G}^\an = \shHom{\struct{X}^\an}{\F^\an}{\G^\an}$ and GAGA I to give,
\begin{align*}
\Hom{\struct{X}}{\F}{\G} & = H^0(X, \shHom{\struct{X}}{\F}{\G}) = H^0(X^\an, \shHom{\struct{X}}{\F}{\G}^\an)
\\
& = H^0(X^\an, \shHom{\struct{X}^\an}{\F^\an}{\G^\an}) = \Hom{\struct{X}^\an}{\F^\an}{\G^\an}
\end{align*}
\end{proof}

\subsection{The Equivalence of ...}

\section{Other Fields}


\end{document}