\documentclass[12pt]{article}
\usepackage{import}
\import{./}{AlgGeoCommands}

\begin{document}

\section{Examples of stable $\infty$-cagtegories}

\subsection{dg-Categories}

\newcommand{\DK}{\mathrm{DK}}
\newcommand{\fin}{\mathrm{fin}}
\newcommand{\Fun}[3]{\mathrm{Fun}_{#1}\left(#2, #3\right)}
\newcommand{\Map}[3]{\mathrm{Map}_{#1}\left(#2, #3\right)}
\newcommand{\Mult}[3]{\mathrm{Mult}_{#1}\left(#2, #3\right)}
\newcommand{\Fin}{\mathrm{Fin}}
\newcommand{\Ob}{\mathrm{Ob}}
\renewcommand{\O}{\mathcal{O}}

Review, let $\cA$ be an abelian cagtegory with enough projectives. Then there is a category $D^-(\cA)$ the derived category of bounded-above.


$\Ch(\cA)$ is naturally a dg-Category meaning it is enriched in $\Ch(\Ab)$. Indeed, if $A, B \in \Ch(\cA)$ then we define,
\[ \Hom{}{A_\bullet}{B_\bullet}_n = \prod_{k} \Hom{}{A_k}{B_{k-n}} \]
with differential,
\[ (\d f)_k = f_{k+1} \circ \d_B + (-1)^{n+1} \d_B \circ f_k \]

Then we check that,
\[ H^0(\Hom{}{A}{B}_\bullet) = \Hom{\Ch{\cA}}{A}{B} \]

\subsection{Program}

Given a dg-category, we get a simplicially enriched category by truncating and then applying Dold-Kan and then apply the homotopy-coherent nerve. 
\bigskip\\
However, this requires checking many steps. We can instead go directly with the following construction. 

\subsection{Construction}

\newcommand{\dg}{\mathrm{dg}}

\begin{defn}
A \textit{dg-category} is a category enriched in $\Ch(\cA)$. This includes the requirement that,
\[ \d{(g \circ f)} = \d{g} \circ f + (-1)^{\deg{g}} g \circ \d{f} \]
which arises from needing to preserve the monoidal structure on $\Ch(\cA)$ given by graded tensor $A \ot B$. 
\end{defn}

We will define a dg-Nerve which goes directly from dg-categories to $\infty$-categories which does not require passing through simplically-enriched categories.

\begin{defn}
Let $C$ be a dg-category. Then the \textit{dg-Nerve} is the simplicial set $N_{\dg}(C)$ where $N_{\dg}(C)_n$ is the set of objects $X_i$ for $i \in \{ 0, \dots, n \}$ and for each ordered set $I = \{ i_- < i_m < \cdots < i_1 < i_+ \}$ for $m \ge 0$ of elements in $\{ 0, \dots, n \}$ we have map,
\[ f_I \in \Map{}{X_{i_-}}{X_{i_+}} \]
such that,
\[ \d{f_I} = \sum_{1 \le j \le m} (-1)^i (f_{I \sm \{ i_j \}} - f_{\{i_j < \cdots < i_+ \}} \circ f_{\{ i_- < \cdots < i_j \}}) \]
and the maps work as follow. If $\alpha : [m] \to [n]$ is monotone. Then the induced map $\alpha^*$ is given by,
\[ \alpha^* (\{ X_i \}, \{ f_I \}) = (\{ X_{\alpha(i)} \}, \{ g_I \}) \]
where,
\[ 
g_J = 
\begin{cases}
f_{\alpha(J)} & \alpha|_J \text{ injective} 
\\
\id_{X_i} & J = \{ j, j'\} \text{ and } \alpha(j) = j'
\\
0 & \text{ else}
\end{cases} \]
\end{defn}

\begin{prop}
For any dg-category $C$ the dg-Nerve $N_{\dg}(C)$ is an $\infty$-category. 
\end{prop}

\begin{proof}
We need to show that inner horns can be filled. However, $\Lambda^n_i \to N_{\dg}(C)$ this is the same data as specifying $\Delta^n \to N_{\dg}(C)$ except we haven't specified all the maps $f_I$. In fact, this has specified the maps for all $I$ except for $I = [n]$ and $I = [n] \sm \{ i \}$. Then we set $f_{[n]} = 0$ and,
\[ f_{[n] \sm \{ i \}} = \sum_{0 < p < n} (-1)^{p-i} f_{\{ p, \dots, n \}} \circ f_{\{0, \dots, p\}} - \sum_{p < p < n, p \neq i} (-1)^{p-i} f_{[n] \sm \{ 0 \}} \]
\end{proof}

\begin{rmk}
$\Hom{N_{\dg}(C)}{X}{Y} = \DK(\tau_{\ge 0} \Map{C}{X}{Y})$ which is the same result we would have gotten from the program applying Dold-Kan to the simplicially-enriched category.
\end{rmk}

\begin{rmk}
Under what conditions do we get a stable $\infty$-category from $N_{\dg}(C)$?
\end{rmk}

\begin{defn}
Let $\cA$ be an abelian category with enough projectives,
$D^+(\cA) = N_{\dg}((\Ch(\cA_{\text{proj}})_{\ge 0})$.
\end{defn}

\begin{prop}[Prop 1.3.2.10]
$D^{-}(\cA)$ is stable. 
\end{prop}

\begin{defn}
We say that $\cA$ is a \textit{Grothendieck abelian category} if $A$ has a generator and small filtered colimits of monomorphisms are monomorphisms.
\end{defn}

\begin{example}
The category of $R$-modules is Grothendieck.
\end{example}

\begin{theorem}
Let $\cA$ be Grothendieck. Then $\Ch(\cA)$ has a model structure where,
\begin{enumerate}
\item cofibrations $M \to N$ are those morphisms which are injective termwise
\item equivalences $M \to N$ are quasi-isomorphisms
\item fibrations are those satisfying the right lifting property wrt the acyclic cofibrations.
\end{enumerate}
\end{theorem}

\begin{prop}[1.3.5.6]
\begin{enumerate}
\item If $M_n$ is injective for all $n$ and $M_n \cong 0$ for $n \gg 0$ then $M_\bullet$ is fibrant.
\item If $M_\bullet$ is fibrant then each $M_n$ is injective. 
\end{enumerate}
\end{prop}

If $M \cA$ and $M' = M[0]$ then there is a fibrant replacement $M[0] \to Q$ where the map is a trivial cofibration this proves enough injectives.

\begin{defn}
Let $\Ch(\cA)^\circ$ be the full subcategory of fibrat objects. Let $D(A) = N_{\dg}(\Ch(\cA)^\circ)$.
\end{defn}

\begin{prop}
$D(\cA)$ is stable and is the $\infty$ unbounded derived category. 
\end{prop}

\newcommand{\dlim}{\varinjlim}
\newcommand{\ilim}{\varprojlim}
\newcommand{\plim}{\varprojlim}

\subsection{Spectra}

\begin{defn}
We say an $\infty$-category is \textit{pointed} if it admits a zero object. 
\end{defn}

Motivation: stable maps,
\[ [X, Y]_s : = \varinjlim_n [\Sigma^n X, \Sigma^n Y] \]
There is a category of topological spaces with stable maps. This gives a triangulated category with $\Sigma$ acting via shift. Constructing this category ``formally'' we have some options,
\begin{enumerate}
\item objects are $(X, n)$ with $X \in \Top$ and $n \in \ZZ$ and morphisms are,
\[ \Hom{}{(X, n)}{(Y, m)} = \dlim_k [\Sigma^{k+n} X, \Sigma^{k+m} Y] \]
which works even for negative $n, m$ becasuse we can choose $k$ large enough. This ``formally inverts'' suspension by giving elemens like $(X, -1)$ which is the de-suspension of $X$

\item construting inifinte loop spaces: a sequence $E_n$ with maps $E_n \iso \Omega E_{n+1}$ so these are progressive deloopings. These are also giving inverses of $\Sigma$.
\end{enumerate}

\begin{defn}
Let $F : C \to D$ be a functor of $\infty$-categories then,
\begin{enumerate}
\item $F$ is \textit{excisive} if psuhout diagrams map to pullback diagrams
\item $F$ is \textit{reduced} if $F(*) = *$. 
\end{enumerate}
\end{defn}

\begin{defn}
Let $\C$ admit finite limits. A \textit{spectrum object} is a reduced excisive functor,
\[ F : S^\fin_* \to \C \]
The $\infty$-category of spectra is,
\[ \Sp(\C) = \Fun{}{S^\fin_*}{\C}_{\text{exc, red}} \subset \Fun{}{S^\fin_*}{\C} \]
where $S^\fin_*$ is the pointed category of finite spaces (full subcategory of $\infty$-category of pointed spaces). 
\end{defn}

\begin{prop}[1.4.2.11]
Let $C$ be a pointed $\infty$-category with finite limits and colimits then $\Omega : \C \to \C$ is an equivalence then $\C$ is stable. 
\end{prop}

\begin{prop}
If $\C$ is a pointed $\infty$-category with finite limits and colimts then $\Sp(\C)$ is stable. 
\end{prop}

\begin{prop}
Let $\C$ be a pointed $\infty$-category with finite limits then there is a tower of $\infty$-categories,
\begin{center}
\begin{tikzcd}
\cdots \arrow[r] & C \arrow[r, "\Omega"] & C \arrow[r, "\Omega"] & C
\end{tikzcd}
\end{center}
and $\Sp(\C)$ is the homotopy limit. 
\end{prop}

Let $\cA$ be an abelian group. Then the Eilenberg-Maclain spaces satisfy $K(A, n-1) \cong \Omega K(A, n)$ and hence defines a spectrum. 

\begin{prop}
Let $\C$ be an $\infty$-category which admits finite limits. The following are equivalent,
\begin{enumerate}
\item $\C$ is a stable $\infty$-category
\item the functor $\Omega^\infty : \Sp(\C) \to \C$ is an equivalence of $\infty$-categories
\end{enumerate}
where $\Omega^\infty$ is the map sending $F \mapsto F(S^0)$ where $S^0 = * \coprod *$.
\end{prop}

\section{$\infty$-operads}

References: Higher Algebra

\subsection{Motivations}

Want the symmetric monoidal category in the $\infty$-setting. 
\bigskip\\
Recall that the definition of a symmetric monidal category is annoying:

\begin{defn}
A symmetric monidal category $(\C, \ot, 1, \alpha, \nu, \beta)$ is,
\begin{enumerate}
\item a $1$-category $\C$
\item a functor $\otimes : \C \times \C \to \C$
\item a natural isomorphism,
\[ \alpha_{X,Y,Z} : X \ot (Y \ot Z) \iso (X \ot Y) \ot Z \]
\item a unit object $1$ with a fixed isomorphism $1 \ot 1 \iso 1$
\item a natural isomorphsim,
\[ \beta_{X,Y} : X \ot Y \iso Y \ot X \]
\end{enumerate}
(this is the easy part, now the bad part) satisfying,
\begin{enumerate}
\item $A \mapsto 1 \ot A$ and $A \mapsto A \ot 1$ are equivalences of categories (then from $A \ot 1 \iso A \ot (1 \ot 1) \iso (A \ot 1) \ot 1$ we see that $A \iso A \ot 1$ by equivalence) 
\item unit should be compatible with associativity,
\begin{center}
\begin{tikzcd}
X \ot (1 \ot Y) \arrow[rr, "\alpha_{1,Y}"] \arrow[rd] & & (X \ot 1) \ot Y \arrow[ld] 
\\
& X \ot Y
\end{tikzcd}
\end{center}

\item some huge nasty diagram making associativity compatible for 4-fold products
\end{enumerate}
\end{defn}

\subsection{Construction}

Let $(\C, \ot)$ be a symmetric monoidal category. Then we can construct a new category $C^{\ot}$ whose objects are $\{ [C_1, \dots, C_n] \}_{C_i \in \C}$ with $n \ge 0$. And the morphisms,
\[ [C_1, \dots, C_n] \xrightarrow{(S, \alpha, f)} [C_1', \dots, C_m'] \]
for $S \subset \{ 1, \dots, n \}$ and $\alpha : S \to \{ 1, \dots, m \}$ and maps $\{ f_j \}^m_{j = 1}$ which are maps $f_j : \ot_{i \in \alpha^{-1}(j)} C_i \to C_j$. The composition law is given by $(S, \alpha, f) \circ (S', \alpha', f')$ in the only reasonable way (WRITE DOWN). 

\begin{rmk}
Notice that the ordering of the object $[C_1, \dots, C_n]$ does not matter. 
\end{rmk}

\begin{defn}
New category $\Fin_*$ whose objects are $\left< n \right> := \{ 1, \dots, n \} \sqcup \{ * \}$ and the morphisms are $\left< n \right> \to \left< m \right>$ with $* \mapsto *$. This is just the category of finite sets with a disjoint basepoint added and the maps must be basepoint preserving. 
\end{defn}

\begin{rmk}
$\Fin_*$ is the category of pointed finite sets and basepoint preserving maps. 
\end{rmk}

\begin{defn}
We have special maps $\rho^i : \left< n \right> \to \left< 1 \right>$ which sends $i \mapsto 1$ and $k \mapsto *$ for $k \neq i$. Then we write $\left< n \right>^\circ = \{1, \dots, n\} = \left< n \right> \sm \{ * \}$.
\end{defn}

\begin{rmk}
The data of a symmetric monoidal category is equivalent to a functor $\C^\ot \to \Fin_*$ given by $[C_1, \dots, C_n] \mapsto \left< n \right>$ satisfying some properties. 
\end{rmk}

\subsection{Colored Operads}

\begin{defn}
A symmetric monoidal $\infty$-category should be a cocartesian fibration $p : \C^\ot \to N(\Fin_*)$ satisfying $\forall n \ge 0$ the collection of $\{ \rho^i \}$ induces $\rho^i_* : \C_{\left< n \right>}^{\ot} \to C^{\ot}_{\left< 1 \right>}$ determining $\C^{\ot}_{\left< n \right>} \cong (\C_{\left< 1 \right>}^{\ot})^{\oplus n}$.
\end{defn}

\begin{rmk}
We will come back and motivate this definition. First we discuss operads which are like categories where we have hom spaces have arbitrary arity, they are not just 2-adic.
\end{rmk}

\begin{defn}
A \textit{colored operad} $\O$ is the following data,
\begin{enumerate}
\item a collection of objects $\Ob(\O)$
\item Hom spaces: given any finite set $I$ and a list of objects $(\{ X_i \}_{i \in I}, Y)$ we get a space $\Mult{\O}{\{ X_i \}_{i \in I}}{Y}$ if $I = \empty$ we get a set $\Mult{\O}{}{Y}$ which is a unit (or something)
\item a composition law, for any map $I \to J$ we get,
\[ \prod_{j \in J} \Mult{\O}{\{ X_i \}_{i \in I_j}}{Y_j} \times \Mult{\O}{\{ Y_j \}_{j \in J}}{Z} \to \Mult{\O}{ \{X_i \}_{i \in J}}{Z} \]
\item $\id_Y \in \Mult{\O}{\{Y \}}{Y}$
\item associativity (DO THIS)
\end{enumerate}
\end{defn}

\begin{rmk}
We use the terminology $\mathrm{Mult}$ because in the case of a symmetric monoidal category we will get an operad with,
\[ \Mult{\O}{\{ X_i \}_{i \in I}}{Y} = \Hom{}{\bigotimes_{i \in I} X_i}{Y} \]
\end{rmk}

\begin{rmk}
From $\O$ we get a $1$-category $\C$ with Objects $\Ob(\C) = \Ob(\O)$ and $\Hom{}{X}{Y} = \Mult{\O}{ \{ X \}}{Y}$.
\end{rmk}

\begin{example}
Given any $1$-category $\C$ we can produce an operad $\O$ on the same objects with,
\[ \Mult{\O}{ \{ X_i \}_{i \in I} }{Y} = 
\begin{cases}
\empty & \# I \neq 1
\\
\Hom{\C}{X}{Y} & \# = 1
\end{cases} \]
This is left-adjoint to the ``underlying category'' functor.
\end{example}

\begin{example}
Given a symmetric monoidal category $(\C, \ot)$ we get an operad on the same objects with,
\[ \Mult{\O}{ \{X_i \}_{i \in I}}{Y} = \Hom{\C}{ \bigotimes_{i \in I} X_i}{Y} \]
\end{example}

\begin{example}
Given a colored operad $\O$, we get a new category $\O^{\ot}$ whose objects are $\{ X_i \}_{i \in I}$ and whose mapping sets are,
\[ \Hom{\O^{\ot}}{ \{ X_i \}_{i \in I} }{ \{Y_j \}_{j \in J} } = \prod_{j \in J} \Mult{\O}{ \{ X_i \}_{i \in I} }{Y_j} \]
In fact, $\O$ is equivalent to the data of the fibration,
\[ \pi : \O^{\ot} \to \Fin_* \]
with some requirements on $\pi$. Indeed we can recover, $\O = \pi^{-1}(\left< 1 \right>)$ and we get $\Mult{\O}{ \{ X_i \}_{i \in I} }{Y}$ by considering maps in $\O^{\ot}$ between the object $\{ X_i \}_{i \in I} \in \pi^{-1}(\left< n \right>)$ and $Y \in \pi^{-1}9\left< 1 \right>)$. 
\end{example}


\subsection{Cocartesian morphisms}

\begin{defn}
Let $p : \C \to \D$ be a functor of $1$-categories. Then $g : X \to Y$ in $\C$ is cocartesian if for all $Z$,
\begin{center}
\begin{tikzcd}
\Hom{\C}{Y}{Z} \arrow[r] \arrow[d] & \Hom{\C}{X}{Z} \arrow[d]
\\
\Hom{\D}{p(Y)}{p(Z)} \arrow[r] & \Hom{\D}{p(X)}{p(Z)}
\end{tikzcd}
\end{center}
is a pullback. 
\end{defn}

\begin{defn}
Let $p : \C \to \D$ be a functor of $\infty$-categories. Then a morpism $g : X \to Y$ in $\C$ is cocartesian if $p$ is an inner fibration and (WHAT)
\end{defn}


\subsection{$\infty$-Operads}

\begin{defn}
$f : \left< m \right> \to \left< n \right>$ in $\Fin_*$ is \textit{inertia} if for $i \in \left< n \right>^\circ$ then $f^{-1}(i)$ consists of \textit{exactly} one element. This means that two elements can only be mapped to the same place if their image is $*$ and also the map is surjective.
\end{defn}

\begin{defn}
An $\infty$-operad is a functor $p : \O^\ot \to N(\Fin_*)$ from an $\infty$-category $\O^\ot$ where we write $\O^{\ot}_{\left< n \right>} = \pi^{-1}(\left< n \right>)$ such that,
\begin{enumerate}
\item if $f : \left< m \right> \to \left< n \right>$ is inertia then every object $C \in \O^{\ot}_{\left< m \right>}$ there exists a $p$-cocartesian morphism $\bar{f} : \C \to \C'$ lifting $f$

\item for $C \in \C^{\ot}_{\left< n \right>}$ and $C' \in \C^{\ot}_{\left< m \right>}$ and $f : \left< m \right> \to \left< n \right>$ in $\Fin_*$ then,
\[ \Map{f}{C}{C'} := (\Map{}{C}{C'})^\circ \]
is the connected component lying over $f$ then,
\[ \Map{f}{C}{C'} \cong \prod_{1 \le i \le n}^f \Map{\rho_i \circ f}{C}{C'} \]
\item $\forall n \ge 0$ the maps $\{ \rho^i_! : \O_{\left< n \right>} \to \O_{\left< 1 \right>}$ induces an equivaence of $\infty$-categories,
\[ \O_{\left< n \right>}^{\ot} \iso \left( \O_{\left< 1 \right>}^\ot \right)^{\oplus n} \]
\end{enumerate}
\end{defn}

\begin{rmk}
We write $\O := \O^{\ot}_{\left< 1 \right>}$ which is called the underlying $\infty$-category of $\O^{\ot}$. 
\end{rmk}

\begin{rmk}
If $\O$ is a colored ($1$-categorical) operad then $N(\O^{\ot}) \to N(\Fin_*)$ is an $\infty$-operad. 
\end{rmk}

\begin{example}
The trivial operad is on the trivial category,
\[ \underline{\mathrm{Triv}} \subset \Fin_* \]
which is the full subcategory on the inertia maps. Then the inclusion map,
\[ N(\underline{\mathrm{Triv}}) \to N(\Fin_*) \]
is an $\infty$-operad. 
\end{example}

\subsection{The Associative Operad}

Let $\E_0^\ot$ be the operad whose objects are $\left< n \right>$ and whose morphism $f : \left< m \right> \to \left< n \right>$ such that $\# f^{-1}(i) \le 1$ for $1 \le i \le n$ (weaker than inertia since it does not have to be surjective). This is the first of our associative operads. 
\bigskip\\
The commutative operad is supposed to be $N(\Fin_*) \to N(\Fin_*)$.

\begin{defn}
A morphism $F : \O_1 \to \O_2$ of operads is a functor $F : \O_1^\ot \to \O_2^\ot$ of $\infty$-categories and a homotopy making the diagram,
\begin{center}
\begin{tikzcd}
\O^\ot_1 \arrow[rr, "F"] \arrow[rd] & & \O^{\ot}_2 \arrow[ld]
\\
& N(\Fin_*)
\end{tikzcd}
\end{center}
\end{defn}

\section{Algebras and Modules}

\subsection{Operad Review}


Perspectives on operads:
\begin{enumerate}
\item Categories with ``many-to-one'' structure: meaning there are higher airity maps $Mult( \{ X_i \}, Y)$

\item For every operad $\O$ get $\O$-monoidal category 

\item For every operad $\O$ get $\O$-algebra object in a symmetric monoidal category

\item for $\O' \to \O$ a map of operads get $\O'$-algebras in $\O$-monoidal categories.
\end{enumerate}

Motivation: $(\Ab, \ot_\Z)$ be the symmetric monoidal category of abelian groups with tensor. A commutative ring is $A \in \Ab$ equipped with maps,
\begin{enumerate}
\item $e : \Z \to A$
\item $m : A \ot A \to A$
\end{enumerate}
such that some diagrams commute,
\begin{center}
\begin{tikzcd}
A \ot A \to A \arrow[r] \arrow[d] & A \ot A \arrow[d]
\\
A \ot A \arrow[r] & A
\end{tikzcd}
\end{center}
etc. We can package all these together into the following construction.

\begin{defn}
A \textit{unital commutative ring} is,
\begin{enumerate}
\item an object $A \in \Ab$
\item for each finite set $I$ a map $m_I : A^{\ot I} \to A$
\end{enumerate}
such that,
\begin{enumerate}
\item if $\# I = 1$ then $m_I = \id$
\item for $\varphi : I \to J$ then $m_I$ is the composition,
\[ A^{\ot I} = \bigotimes_{i \in J} A^{\ot \varphi^{-1}(j)} \xrightarrow{\bigotimes_{j \in J} \m_{\varphi^{-1}(j)}} A^{\ot J} \xrightarrow{m_J} A \]
\end{enumerate}
\end{defn}

\begin{rmk}
Commutativity arrises from the swapping map $\varphi : \{ 1, 2\} \to \{ 1, 2 \}$.
\end{rmk}

\newcommand{\comb}{\mathrm{comb}}
\newcommand{\comp}{\mathrm{comp}}

\begin{defn}
$\ord(I)$ is the set of linear orders on $I$. There is a ``combine orderings'' map,
\[ \comb : \ord(J) \times \prod_{j \in J} \ord(\varphi^{-1}(j)) \to \ord(I) \]
given $\varphi : I \to J$.
\end{defn}

\begin{defn}
A \textit{unital associative ring} is,
\begin{enumerate}
\item an object $A \in \Ab$
\item for each finite set $I$ and $o \in \ord(I)$ a map $m_{I,o} : A^{\ot I} \to A$
\end{enumerate}
such that,
\begin{enumerate}
\item if $\# I = 1$ then $m_I = \id$
\item for $\varphi : I \to J$ then $m_{I, \comb(o, o_j)}$ is the composition,
\[ A^{\ot I} = \bigotimes_{i \in J} A^{\ot \varphi^{-1}(j)} \xrightarrow{\bigotimes_{j \in J} \m_{\varphi^{-1}(j)}, o_j} A^{\ot J} \xrightarrow{m_J, o} A \]
\end{enumerate}
\end{defn}

\begin{rmk}
What if we want to define a \textit{non-unital} associative ring? In this case we just require our sets $I$ to be nonempty. Or alternatively, let,
\[ \ord'(I) = 
\begin{cases}
\ord(I) & I \neq \empty 
\\
\empty & I = \empty 
\end{cases}\]
Replacing $\ord$ by $\ord'$ gives the definition of a non-unital associative ring. 
\end{rmk}

\begin{defn}
For a colored operad $\O^{\ot}$ which consists of,
\begin{enumerate}
\item a set of colors $\O$ 
\item for each collection $\{ X_i \}_{i \in i}$ and $Y$ of colors there is a set,
\[ \Mult{\O}{ \{ X_i \}_{i \in I}}{Y} \]
satisfying some associativity and unital relations. 
\end{enumerate} 
and a symmetric monoidal category $(\C, \ot)$ an \underline{$\O$-algebra object} in $(\C, \ot)$ is the data of,
\begin{enumerate}
\item for each $X \in \O$ an object $A_X \in \C$
\item for each $m : \{ X_i \}_{i \in I} \to Y$ a morphism,
\[ f_m : \bigotimes_{i \in I} A_{X_i} \to A_Y \]
\end{enumerate}
satisfying,
\begin{enumerate}
\item if $m = \id_X \in \Mult{\O}{ \{ X \} }{X}$ then $f_m = \id_{A_X}$

\item if $\varphi : I \to J$ and $m \in \Mult{\O}{ \{ Y_j \}_{j \in J}}{Z}$ and $m_j \in \Mult{\O}{ \{ X_i \}_{i \in \varphi^{-1}(j)}}{Y_j}$ then $f_{\comp(m, \{ m_j \})}$ equals the composition,
\[ \bigotimes_{i \in I} A_{X_i} \xrightarrow{\otimes_{j \in J} f_{m_j}} \bigoplus_{j \in J} A_{Y_j} \xrightarrow{f_m} A_Z \]
\end{enumerate}
\end{defn}

\begin{rmk}
An $\O$-algebra object in $\C$ is the same as a map of operads $\O^\ot \to \C^\ot$. 
\end{rmk}

\begin{rmk}
There is a notion of maps of operads,
\[ \{ \text{symmetric monoidal cat} \} \embed \{ \text{operads} \} \]
An $\O^\ot$-algebra object of $\C^\ot$ is a map of operads $\O^\ot \to \C^\ot$. Maps of operads are diagrams,
\begin{center}
\begin{tikzcd}
\O^\ot \arrow[r] \arrow[d] & \O^{\ot'} \arrow[d]
\\
N(\Fin_*) \arrow[r, equals] & N(\Fin_*)
\end{tikzcd}
\end{center}
that takes cotartesian lifts of inert maps to cocartesian lifts. 
\end{rmk}

\subsection{Little Cubes Operad}

\renewcommand{\E}{\mathbb{E}}

For $n \ge 0$ construct an $\infty$-operad $\E_n^{\ot}$. Consider $D^n \subset \RR^n$ unit disk. There is a unique color $* \in \O$ and then define (writing $I$ for $\{ * \}_I$),
\[ \Mult{}{I}{*} = \{ \text{embeddings } \coprod_{i \in I} D^n \to D^n \text{ arising from scaling and translation} \} \]
There is a composition map, for $\varphi : I \to J$,
\[ \Mult{}{J}{*} \times \prod_{j \in J} \Mult{}{\varphi^{-1}(j)}{*} \to \Mult{}{I}{*} \]
which is continuous. Then we can take the topological nerve to get an $\infty$-operad $\E_n^{\ot}$. 

\begin{rmk}
$\E_1^\ot$ is discrete and $\E^{\ot}_1 \cong \mathrm{Assoc}^\ot$ (defining unital associative algebra) which is the operad of finite sets with orderings. 
\bigskip\\
Then $\E_0^{\ot}$ is trivial which just imposes the existence of an object $u : \Z \to A$ so we get pointed objects.
\end{rmk}

\begin{defn}
$\E^\ot_{\infty} = [N(\Fin_*) \to N(\Fin_*)]$ as an operad. Meaning $\Mult{\E_\infty^{\ot}}{I}{*} = \{ * \}$. This is because as we take the limit of $n$ for the morphism sets of $\E_n^{\ot}$ with fixed $I$ the spaces become weakly contractible.
\end{defn}

There are maps of operads $\E_0^{\ot} \to \E_1^{\ot} \to \E_2^{\ot} \to \cdots \to \E^{\ot}_{\infty}$. Therefore, I can always restrict an $\E_n^\ot$-algebra to a lower-order algebra. 

\newcommand{\Alg}{\mathrm{Alg}}
\newcommand{\gp}{\mathrm{gp}}

\begin{rmk}
Recall that $\S$ is the $\infty$-category of spaces.
\end{rmk}

\begin{theorem}[May]
Inside the monoidal category $(\S, \times)$. Then there is a functor,
\[ \S_* \xrightarrow{\Omega^n} \Alg_{\E^\ot_n}(\S) \] 
This induces an equivalence for $n \ge 1$,
\[ \S_{*, \ge n} \iso \Alg_{\E^\ot_n}^{\gp}(\S) \]
where $\S_{*, \ge n}$ is the $\infty$-category of $n$-connected pointed spaces and $\Alg_{\E^\ot_n}^{\gp}(\S)$ is the $\infty$-category of grouplike $\E_n^{\ot}$-algebras in spaces where we say that an algebra $A$ is grouplike if $\pi_0(A)$ with its induced monoid structure is a group. Furthermore, there is an equivalence,
\[ \Sp(\S_*)_{\ge 0} \iso \Alg_{\E_\infty^\ot}(\S) \]
between connective spectra and $\E_\infty^\ot$-algebras. 
\end{theorem}

\subsection{Limits and Colimits}

\begin{theorem}
If $\C$ has all small limits then $\Alg_{\O}(\C)$ also has all small limits and limits are computed ``objectwise''. 
\end{theorem}

\begin{theorem}
If $\C$ has all small colimits and $X \ot -$ preserves them then $\Alg_{\E^\ot_{\infty}}(\C)$ has small colimits. 
\end{theorem}

\subsection{Modules}

\newcommand{\CAlg}{\mathrm{CAlg}}

If $A \in \CAlg(\C)$ then there is a category $\Mod{A}{\C}$.

\begin{rmk}
$\Mod{A}{\C}$ does \textit{not} have a symmetric monoidal structure but only an operad structure. 
\end{rmk}

\begin{theorem}
If $A \in \CAlg(\C)$ then,
\[ \CAlg(\Mod{A}{(\C)}) \cong \CAlg(\C)_{A / } \]
If $B$ is an algebra over $\Mod{A}{(\C)}$ corresponding to some $\\overline{B} \in \CAlg(\C)_{A / }$ then,
\[ \Mod{B}{(\Mod{A}{(\C)})} \cong \Mod{\overline{B}}{(\C)} \]
\end{theorem}

\begin{theorem}
\begin{enumerate}
\item Limits in $\Mod{A}{(\C)}$ can be computed in $\C$
\item of $\C$ is presentable and $X \ot -$ preserves al l small colimits then $\Mod{A}{(\C)}$ is symmetric monoidal, presentable, and $\ot$ commutes with colimits. 
\end{enumerate}
\end{theorem}

\section{Ring Spectra}

Recalll a spectrum object in $S_*$ os an $\infty$-functor,
\[ F : S_*^\fin \to S_* \]
such that,
\begin{enumerate}
\item $F$ sends homotopy pushouts to pullbacks
\item $F(*) = *$.
\end{enumerate}

\begin{rmk}
For each $n$ there is a pushout square,
\begin{center}
\begin{tikzcd}
S^n \arrow[r] \arrow[d] & * \arrow[d]
\\
* \arrow[r] & S^{n+1}
\end{tikzcd}
\end{center}
which gives a pullback square,
\begin{center}
\begin{tikzcd}
F(S^n) \arrow[r] \arrow[d] & * \arrow[d]
\\
* \arrow[r] & F(S^{n+1})
\end{tikzcd}
\end{center}
and thus $F(S^n) = \Omega F(S^{n+1})$. Since every object of $S_*^{\fin}$ is a finite colimit of spheres therefore the data of $F$ is equivalent up to homotopy to the sequence $\{ F(S^n) \}$ along with the data of equvalenes $F(S^n) \iso \Omega F(S^{n+1})$. This is classically what is known as an $\Omega$-spectrum.
\end{rmk}

\begin{defn}
A \textit{spectrum} is a sequence of pointed spaces $\{ X _n \}_{n \ge 0}$ along with maps $\Sigma X_n \to X_{n+1}$ (equivalently $X_n \to \Omega X_{n+1}$).
\end{defn}

\begin{example}
Some spectra,
\begin{enumerate}
\item $\S = \{ S^n \}_{n \ge 0}$ is not an $\Omega$-spectrum
\item for $A \in \Ab$ we have $H A = \{ K(A, n) \}_{h \ge 0}$ is an $\Omega$-spectrum

\item of $\{ Y_n \}_{n \ge 0}$ is any sequence of spaces then define $X_0 = Y_0$ and $X_{n+1} = \Sigma X_n \vee Y_{n+1}$ and this defines a spectrum.
\end{enumerate}
\end{example}

How do we make this into a category of specta? If $X, Y$ are $\Omega$-spectra then,
\[ \Hom{\mathrm{hSp}}{X}{Y} = \left\{ f_n : X_n \to Y_n \middle| 
\begin{tikzcd}
X_n \arrow[r, "f_n"] \arrow[d] & Y_n \arrow[d]
\\
\Omega X_{n+1} \arrow[r, "\Omega f_{n+1}"] & \Omega Y_{n+1} 
\end{tikzcd} \right\} \]

If $X, Y$ are \textit{not} $\Omega$-spectra then,
\[ \Hom{\text{hSp}}{X}{Y} = \dlim_{X' \subset X} \Hom{}{X'}{X} \]
where $X' \subset X$ is a weak homotopy equivalence where we define weak homotopy equivalence using the following notion of homotopy groups.

\begin{defn}
if $X$ is spectrum $n \in \ZZ$ then define,
\[ \pi_n(X) = \dlim_k \pi_{n+k}(X_k) \]
\end{defn}

\begin{example}
$\pi_n(\S) = \pi_n^s(\S) = \pi_{2n + 2}(S^{n+2}$ by Freudenthal suspension.
\end{example}

\begin{example}
\[ \pi_n(HA) = 
\begin{cases}
A & n = 0
\\
0
\end{cases} \]
\end{example}

\begin{example}
Homotopy groups may be supported in negative degrees. Indeed consider,
\[ X_n = S^n \vee S^{n-1} \vee \cdots \vee S^1 \]
then $\pi_k(X_n) \neq 0$ for all $k \in \Z$ using Hilton-Milnor theorem. 
\end{example}

\begin{prop}
The inclusion $N(\Ab) \to \Sp$ sending $A \mapsto HA$ is fully faithful.
\end{prop}

\begin{proof}
Let's just check this $\mathrm{hSp}$. Point is to compute $[K(A, n), K(B, n)]$. This is,
\[ [K(A, n), K(B, n)] = H^n(K(A, n), B) = \Hom{}{H_n(A, n), \Z}{B} = \Hom{}{\pi_n(K(A, n))}{B} = \Hom{}{A}{B} \]
using Hurewicz's theorem. 
\end{proof}

\begin{defn}
There is a natural $t$-structure on $\Sp$ which is $\Sp^{\ge 0} = \{ X \mid \pi_n(X) = 0 \quad n < 0 \}$ with $\Sp^{\le 0}$ defined similarly. 
\end{defn}

\newcommand{\heart}{\heartsuit}
\newcommand{\EE}{\mathbb{E}}

\begin{prop}
$(\Sp^{\ge 0}, \Sp^{\le 0})$ is a $t$-structure and its heart $\Sp^{\heart} = N(\Ab)$ meaning $X \in \Sp^{\heart}$ satisfies $X \cong H \pi_0(X)$.
\end{prop}

\begin{proof}
This is just because its heart is objects with trivial higher homotopy groups (setlike). 
\end{proof}

\subsection{Smash Product}

For $X, Y \in \Top_*$ then $X \wedge Y = (X \times Y) / (X \vee Y)$.

\begin{example}
$S^0 \wedge X \cong X$ and $S^1 \wedge X \cong \Sigma X$ (by definition). Then $S^m \wedge S^n \cong S^{m+n}$ because $(\RR^m)_{\infty} \wedge (\RR^n)_{\infty} \cong (\RR^{m+n})_{\infty}$.
\end{example}

\begin{example}
There is a weird sign,
\begin{center}
\begin{tikzcd}
S^1 \wedge S^1 \arrow[d] \arrow[r, "\text{flip}"] & S^1 \wedge S^1 \arrow[d]
\\
S^2 \arrow[r, "-1"] & S^2
\end{tikzcd}
\end{center}
because it is orientation reversing. 
\end{example}

\begin{prop}
Some properties,
\begin{enumerate}
\item \[ \Hom{\Top_*}{X \wedge Y}{Z} \cong \Hom{\Top_*}{X}{\Hom{\Top_*}{Y}{Z}} \]

\item $X \wedge Y \cong Y \wedge X$

\item $(X \wedge Y) \wedge Z \cong X \wedge (Y \wedge Z)$. 
\end{enumerate}
\end{prop}


\begin{theorem}[HA, 4.8.2.19]
There exists a symmetric monoidal structure $\ot : \Sp \times \Sp \to \Sp$ with unit $\S$ which commutes with small colimits in both variables. If $\C$ is a symmetric monoidal $\infty$-cat, stable and presentable and $\ot : \C \times \C \to \C$ preserves small colimits in each variable then there exists a unique up to homotopy symmetric monoidal functor $F : \Sp^\ot \to \C^\ot$ such that the underlying $\Sp \to \C$ preserves small colimts. 
\end{theorem}

\begin{rmk}
Note that $H A \ot H B \not\cong H(A \ot B)$ this acts more like a derived tensor product.
\end{rmk}

\begin{example}
$\S \wedge \S \to \S$ is an isomorphism and gives the trivial ring spectrum. 
\end{example}

If $R$ is an $\EE_1$-ring then,
\[ \pi_* R = \bigoplus_{n \in \ZZ} \pi_* R \]
is a graded ring. Then $\pi_n R = [\S[n], R]$ with $\S[n]_k = \S_{n+k}$ and we have,
\[ [\S[n], R] \times [\S[m], R] \to [\S[n] \ot \S[m], R \ot R] \to [\S[n+m], R] = \pi_{n+m}(R) \]
a multiplication map. 

\begin{rmk}
Note that if $R$ is an $\EE_\infty$-ring then $\pi_* R$ is graded commutative from the fact that $\S[n] \ot \S[m]$ is antisymmetric. 
\end{rmk}

Notions of left (right) module. All certain algebra objects in $\Sp$. The left-module operad $\underline{\text{LM}}$ has two colors $A, M$ and,
\[ \Mult{\text{LM}}{ \{ X_i \}_{i \in I}}{A} = 
\begin{cases}
\ord(I) & X_i = A \text{ for all } i
\\
\empty & \text{else} 
\end{cases} \]
and likewise,
\[ \Mult{\text{LM}}{\{X_i\}_{i \in I}}{M} = 
\begin{cases}
\ord(I) & M \text{ is largest if all but exactly one are } M
\\
\empty & \text{else}
\end{cases} \]

A left module is an $\text{LM}$-algebra object of $\Sp$,
\begin{center}
\begin{tikzcd}
\LMod_R \arrow[r] \arrow[d] & \LMod \arrow[d]
\\
\{ R \} \arrow[r, hook] & \Alg_{\EE_1}(\Sp) 
\end{tikzcd}
\end{center}

\begin{prop}
We have,
\begin{enumerate}
\item $\LMod_R$ is stable
\item natural $t$-structure (connective and anti-connected)
\item if $\pi_n R = 0$ for $n \neq 0$ then $\LMod_R \cong \D(\Mod_{\pi_0(R)})$ preserving $t$-structures.
\end{enumerate}
\end{prop}

Let $R$ be a discrete commutative ring then $\Alg^{\dg}(R)$ has a model structure with,
\begin{enumerate}
\item weak equivalences are quasi-isomorphisms
\item fibrations are levelwise surjective 
\end{enumerate}

\begin{prop}
$N(\Alg^{\dg}(R)^c][W^{-1}] \cong \Alg_{\EE_1}(R)$ where $c$ means the category of cofibrant objects. If $\Q \subset R$ then,
\[ N(\CAlg^{\ad}(R)^c)[W^{-1}] \cong \Alg_{\EE_\infty}(R) \]
with graded commutative on the left.
\end{prop}

\section{Feb. 23}

\begin{defn}
Let $R$ be connecteive then $P \in \LMod_R^\cn$ is \textit{projective} if $\Hom{}{P}{-} : \LMod_R^\cn \to \S$ preserve gemoetric realization.
\end{defn}

\begin{rmk}
\begin{enumerate}
\item in classical setting geometric realization is coequalizer so this recoveres the usual definition of preserving colimits

\item $\LMod_R$ of all not necessarily connective objects has no nonzero projective objects. 
\end{enumerate}
\end{rmk}

\begin{prop}
The following are equivalent,
\begin{enumerate}
\item $P$ is projective

\item for all $Q \in \LMod_R^\cn$ and $i > 0$ we have $\Ext{i}{R}{P}{Q} := \pi_0(\Hom{}{P}{Q[i]}) = 0$

\item Given fiber sequence,
\[ N' \to N \to N'' \]
the map $\Ext{0}{R}{P}{N} \to \Ext{0}{R}{P}{N''}$ is surjective.
\end{enumerate}
\end{prop}

\begin{prop}
TFAE:
\begin{enumerate}
\item $P$ is projective

\item there exists a free module $R$-module $M$ with $P$ a retract of $M$ meaning $P \to M \to P$ with $P \to P$ an equivalence. 
\end{enumerate}
\end{prop}

\begin{proof}
First show (a) $\implies$ (b). There exists $R^{\oplus I} \to P$ such that $\pi_0(R^{\oplus n}) \onto \pi_0(P)$ is a surjection. Consider the fiber sequence,
\[ N \to R^{\oplus I} \to P \]
then $N$ is connective by the surjection of $\pi_0$. Consider $\Hom{R}{P}{-}$ applied to the fiber sequence, by surjection on $\Ext{0}{R}{P}{-}$ we get $P \to R^{\oplus I}$ satisfying the required properties. 
\bigskip\\
For (b) $\implies$ (a) we have projectivity is preserved by retract. For,
\[ P \to S \to P \]
then $\Ext{i}{R}{P}{Q}$ is a retract of $\Ext{i}{R}{S}{Q}$ then STP free module are projective.  
\end{proof}

\begin{rmk}
What are the examples of ring spectra:
\begin{enumerate}
\item $K(A)$ for $A$ a discrete ring
\item $\S$
\item simplicial commutative rings.
\end{enumerate}
\end{rmk}

\begin{rmk}
In the followign definition we don't need any connectivity assumptions.
\end{rmk}

\begin{defn}
$M$ is flat over $R$ if,
\begin{enumerate}
\item $\pi_0(M)$ is a flat $\pi_0(N)$-module
\item $\pi_m(R) \ot_{\pi_0(R)} \pi_0(M) \iso \pi_n(M)$ for all $n$.
\end{enumerate}
\end{defn}

\begin{rmk}
Flatness is closed under coproduct, retract, filtered colimits. If $R$ is connective then projective implies flat. 
\end{rmk}

\begin{prop}
Let $N, R$ be connective. The following are equivalent,
\begin{enumerate}
\item $N$ is flat
\item if $M$ is a discrete right $R$-module then $M \ot_R N$ is discrete.
\end{enumerate}
\end{prop}

\begin{proof}
Spectral sequence,
\[ \Tor{\pi_* R}{p}{\pi_* M}{\pi_* N}_q = \pi_{p+q}(M \ot_R N) \]
Then (a) $\implies$ (b) because LHS = 0 if $p \neq 0$ and thus,
\[ \pi_p(M \ot_R N) = (\pi_* M \ot_{\pi_* R} \pi_* N)_p = \cong (\pi_* M \ot_{\pi_0(R)} \pi_0(N))_p \]
For (b) $\implies$ (a) we use $- \ot_R N : \RMod_R \to \S$ and that $\RMod_R^{\heart} = \Mod_{\pi_0(R)}$. Then (b) says that we restrict to,
\[ - \ot_R N : \Mod_{\pi_0(R)} \to \Set \]
which in particular is a map to $\Set$. However, $-\ot_R N$ is exact (preserves fiber sequences) and hence is exact on the heart. Then $- \ot_R N = - \ot_{\pi_0(R)} \pi_0(N)$ (using the spectral sequence and the fact that $M \ot_R N$ is discrete for $M$ discrete) and thus is exact meaning $\pi_0(N)$ is flat over $\pi_0(R)$. The rest uses the spectral sequence. 
\end{proof}

\begin{lemma}
A map $f : M \to N$ of flat $R$-modules is an equivalence iff $\pi_0(f) : \pi_0(M) \to \pi_0(N)$ is an isomorphism.
\end{lemma}

\begin{prop}
Let $R$ be connective and $M / R$ is flat then,
\[ M \text{ is projective} \iff \pi_0(M) \text{ is projective over } \pi_0(R) \]
\end{prop}

\begin{proof}
We show a weaker version. If $\pi_0(M)$ is free over $\pi_0(R)$ then can find a free module $R^{\oplus n} \to M$ which is an isomorphism on $\pi_0$. Then apply lemma to conclude. 
\end{proof}

\subsection{Localization}

Let $R$ be an $\EE_\infty$-ring then $\pi_*(R)$ is graded-commutative. Consider $S \subset \pi_*(R)$ set of homog. elements closed under multiplication and containing $1$. Then,
\begin{enumerate}
\item $M$ is $S$-nilp if all $x \in \pi_m(M)$ are killed by some $s \in S$

\item $M$ is $S$-local if for each $s \in S$ the map $\pi_* M \xrightarrow{s} \pi_* M$ is an isomorphism (not necessarily a graded map)
\end{enumerate}
This produces two subcategories $\LMod_R^{\text{S-nilp}}$ and $\LMod_R^{\text{S-Loc}}$. We want some adjoints which will be localizations.
\begin{enumerate}
\item $\LMod_R^{\text{S-nilp}}$ is stable $\infty$-category, closed under small colimits generated under colimits by $R / Rs [n]$ for $s \in S$. If $s \in \pi_d(R)$ then this arises from,
\[ R[d] \xrightarrow{s} R \to R / R s \]

\item $M \in \LMod_R^{\text{S-loc}} \iff $ for all $s \in S$ and $n \in \ZZ$ then $\Hom{}{R/R_s[n]}{N}$ is contactible iff $\forall M \in \LMod^{\text{S-nilp}}$ we have $\Hom{R}{M}{N}$ contractible.
\end{enumerate}

(1) gives a right adjoint $G : \LMod_R \to \LMod_R^{\text{S-nilp}}$ to the inclusion. Then we take a fiber sequence,
\[ G(M) \to M \to S^{-1} M \]
defining $S^{-1} M$ and,
\[ \Hom{}{N}{G(M)} \iso \Hom{}{N}{M} \to \Hom{}{N}{S^{-1} M} \]
so the last term is contractible proving that $S^{-1} M \in \Mod_R^{\text{S-loc}}$. 

\begin{rmk}
The functor $S^{-1}(-)$ gives a left adjoint to the inclusion. 
\end{rmk}

\begin{prop}
$(\LMod_R^{\text{S-nilp}, \LMod_R^{\text{S-loc}})$ gives a $t$-structure on $\LMod_R$ with trivial heart. 
\end{prop}

\begin{rmk}
$\pi_*(S^{-1} M) = S^{-1} \pi_*(M)$. 
\end{rmk}

\section{Higher Algebraic Geometry}

\subsection{Other Flavors of higher AG}

We need a notion of what a ``higher ring'' is to define higher affine schemes.

\begin{defn}
Fix a discrete commutative ring $R$. Then consider the following types of higher $R$-algebras,
\begin{enumerate}
\item simplicial $R$-algebras (a simplicial object in $R$-Alg)
\item commutative dg-algebras over $R$
\item $\EE_\infty$-algebras over $R$.
\end{enumerate}
\end{defn}

\begin{rmk}
de-algebras over a ring $R$ which does not contain $\QQ$ is ``bad'' according to Lurie. When $\QQ \subset R$ then it is equivalent to $\EE_\infty$-algebras over $R$. Therefore, the only purpose, in the modern perspective, of considering the dg-algebras is to give concrete models for everything in the case $\QQ \subset R$, the theory works less nicely in general. 
\end{rmk}

\begin{defn}
Fix $R \in \CAlg^\heart$ write $\Poly_R$ for the $1$-category of $R$-algebras isomorphic to $R[x_1, \dots, x_n]$. Define the full subcategory, $\CAlg_R^\Delta$ of functors,
\[ \Poly^\op_R \to \Space \]
preserving finite products. 
\end{defn}

\begin{rmk}
Given $F : \Poly_R^\op \to \Space$ consider $A = F(R[x])$. Then pulling back along $R[x] \to R[y,z]$ sending $x \mapsto yz$ gives a map $A \times A \to A$ making $A$ into a ring space. Moreover the other maps make $A$ an $R$-module in spaces.
\end{rmk}

\begin{rmk}
For the simplicial model structure on the simplicial category of $R$-algebras when you take nerve of the fibrant-cofibrant objects you get $\CAlg_R^\Delta$. 
\end{rmk}

\begin{theorem}[SAG, 25.1.2.2]
There is a functor $\theta : \CAlg_R^\Delta \to (\CAlg_R^\cn)_{R/}$ preserving all limits and colimits. Moreover, $\theta$ detects isomorphisms and is an equivalence if $R \supset \Q$.
\end{theorem}

\begin{rmk}
Given $x \in A$ for $\CAlg_R^\Delta$ there is a canonical way of getting a squaring map from pulling back along $R[x] \to R[x]$ mapping $x \mapsto x^2$. However, for $\CAlg_R$ there is $B \Sigma_2$ ways of squaring because you have to choose a set with two elements to define the map. 
\end{rmk}

\subsection{Spectral Schemes}

\begin{defn}
A \textit{spectrally ringed space} $(X, \struct{X})$ is a topological space $X$ and an $\infty$-sheaf of $\EE_\infty$-ringed spectra 
\end{defn}

\begin{defn}
An $\infty$-sheaf is a presheaf $\F$ on $X$ valued in an $\infty$-category $\C$ with $U = \bigcup U_\alpha$ then,
\[ \F(U) = \ilim_{\substack{V \susbet U_\alpha \\ \text{ for some \alpha}}} \F(V) \]
or equivalently,
\[ \F(U) = \lim \left( \prod \F(U_\alpha) \to \prod \F(U_\alpha \cap U_\beta) \to \cdots \right) \] 
\end{defn}

\begin{prop}
Let $A \in \CAlg_R$. There is a (hyper) sheaf $\struct{}$ valued in $\CAlg$ on $| \Spec{\pi_0(A)} |$ such that,
\[ \struct{}(|\Spec{(\pi_0 A)[f^{-1}]|) = A[f^{-1}] \]
for all $f \in \pi_0(A)$. 
\end{prop}

\begin{proof}
There is a fact in HTT that it suffices to check the sheaf condition on the basis for the topology if the base satisfies that the intersection of two sets in the base is in the base (in the $\infty$-setting this is actually important for some reason). Therefore, it suffices to check that,
\[ A = \lim \left( \prod A[f_i^{-1}] \to \prod A[f_i^{-1} f_j^{-1}] \to \cdots \right) \]
Note that,
\[ A \to \prod A[f_i^{-1}] \]
is flat and faithfully flat on $\pi_0$. Therefore, it suffices to show equivalence after base change by $A \to A[f_i^{-1}]$ but this is clear after we base change. 
\end{proof}

\begin{rmk}
Even in $A \in \CAlg^\heart$ then $\struct{\Spec{A}}$ is not discrete. Indeed,
\[ \pi_n(\struct{\Spec{A}}(U)) = H^{-n}(U, (\pi_0(\struct{X})|_U) \]
but the ``classical sheafification'' is zero. 
\end{rmk}

\begin{rmk}
This is because usual sheaves are not $\infty$-sheaves. We have to sheafify and when we do this the sheaf of rings stops being discrete. 
\end{rmk}

\begin{defn}
A \textit{non-connective spectral scheme} is a spectrally ringed space $(X, \struct{X})$ that locally isomorphic to $(\Spec{A}, \struct{\Spec{A}})$. A morphism is a locally spectral morphism of spectrally ringed spaces.
\end{defn}

\begin{example}
If we take $\P^1 \to \P^2$ a line and take $\P^1 \times_{\P^2} \P^1$ in the category of spectral schemes this is non-classical.  Consider,
\begin{center}
\begin{tikzcd}
k[x,y] \arrow[r] \arrow[d] & k[x] \arrow[d]
\\
k[x] \arrow[r] & A
\end{tikzcd}
\end{center}
then $\pi_0(A) = k[x]$ and $\pi_1(A) = \Tor{k[x,y]}{1}{k[x]}{k[x]} = k[x]$. This comes from the (spectral) spectral sequence,
\[ E^2_{p,q} = \Tor{\pi_*(A)}{p}{\pi_* B}{\pi_* C}_q \implies \pi_* (B \ot_A C) \]
\end{example}

\begin{defn}
$A \to B$ is \etale if it is flat and $\pi_0(A) \to \pi_0(B)$ is \etale. 
\end{defn}

\begin{theorem}[HA, 7.5.0.6]
The functor $\pi_0 : \CAlg_{A/}^{\et} \to (\CAlg^\heart)^{\et}_{\pi_0(A) /}$ is an equivalence. This is the map taking \etale $A$-algebras to \etale $\pi_0(A)$-algebras. 
\end{theorem}

\begin{defn}
A \textit{spectrally ringed topos} is a pair $(\X, \struct{\X})$ where $\X$ is an $\infty$-topos and $\struct{\X}$ is a sheaf on $\X$ valued in $\CAlg$.  A sheaf on $\X$ is a functor $\X^\op \to \CAlg$ preserving all small limits. 
\end{defn}

\newcommand{\Spet}{\mathrm{Sp}\et}

\begin{defn}
For $A \in \CAlg$ define $\Spet{A}$ to be $\Space$-valued sheaves on the small \etale site with the forgetful map $R / A \mapsto R$. 
\end{defn}

\begin{defn}
A \textit{non-connective spectral Deligne-Mumford stack} is a sepctrally ringed topos that locally is isomorphic to $\Spet{A}$. 
\end{defn}

\begin{defn}
\textit{Locally} in a topos means there exist elements $U_i \in \X$ such that $\coprod U_i \to 1_\X$ is an effective epi and $(\X_{/U_i}, \struct{}|_{\X_{/U_i}})$ are isomorphic to $\Spet{A}$. 
\end{defn}

\begin{rmk}
$\Sch \embed \Sp\Sch \embed \Sp\Sch^\nc \embed \Sp\DM^\nc$.
\end{rmk}

\section{Cotangent Complex}

\begin{defn}
Let $R$ be a ring (a classical ring i.e. in $\CAlg^\heart$. For each polynomial ring $A = R[x_1, \dots, x_n]$ define $\LL_{A/R} = A \left< \d{x_1}, \dots, \d{x_n} \right>$. Then then extend this to,
\[ \L_{(-)/R} : \CAlg_R^\Delta = P_\Sigma(\Poly_R) \to \Mod_R \]
\end{defn}

\begin{rmk}
The category $\CAlg_R^\Delta$ is functors $\Poly_R^\op \to \S$ preserving finite products. In particular, for any $R$-algebra, the Yoneda functor gives such an example. Therefore, there is a fully-faithful embedding $\CAlg_R^\heart \embed \CAlg_R^\Delta$.
\end{rmk}

\begin{rmk}
This construction is a bit unnatural, it goes essentially through polynomial rings. From the perspective of higher algebra, the cotangent complex should represent something.
\end{rmk}

\begin{rmk}
Why is $\Omega_{B/A}$ bad? It is defined via,
\[ \Der{A}{B}{M} \cong \Hom{B}{\Omega_{B/A}}{M} \]
but we're testing against discrete $B$-modules $M$ so there's no hope for seeing `higher information''. However, if we allow for nondiscrete $M$ (say complexes) then the representing object will be $\LL_{B/A}$.
\end{rmk}

\subsection{Relative Adjunction}

Motivation: if $M$ is a $B$-module, define $B \oplus M$ as a $B$-algebras that is a square-zero thickening of $B$ meaning the multiplication is,
\[ (b, m) \cdot (b', m') = (bb', bm' + b' m) \]
Then, $\Der{A}{B}{M}$ is the set of $A$-algebra sections of $B \oplus M \to B$.

\begin{rmk}
Therefore, the strategry is to forget about derivations and instead understand these extensions $B \oplus M \to B$.
\end{rmk}

\begin{defn}
Define the category, 
\[ \CAlg^{\heart+} = \{ (A, M) \mid A \in \CAlg^\heart, M \text{ is an } A\text{-module} \} \]
where the maps are,
\[ \Hom{}{(A, M)}{(B, B)} = \{ (f : A \to B, g : M \to N) \} \]
where we require that $g$ is linear over $f$. Then we get a functor,
\[ G : \CAlg^{\heart+} \to \Fun{}{\Delta^1}{\CAlg^\heart} \]
given by sending,
\[ (A, M) \mapsto (A \oplus M \to A) \]
Then the fiber of $\ev_1 : \Fun{}{\Delta^1}{\CAlg^\heart} \to \CAlg^\heart$ composed with $G$ over $A$ is the category of $A$-modules. 
\end{defn}

Consider the diagram,
\begin{center}
\begin{tikzcd}
\CAlg^{\heart +} \arrow[rd]  \arrow[rr, "G"] & & \Fun{}{\Delta^1}{\CAlg} \arrow[ld, "\ev_1"]
\\
& \CAlg^{\heart}
\end{tikzcd}
\end{center}

\begin{prop}
Then $G$ has a left adjoint given by $(A \to B) \mapsto (B, B \ot_A \Omega_{A/\Z})$.
\end{prop}

\begin{rmk}
This uses the following proposition.
\end{rmk}

\begin{prop}[HA, 3.2.6]
If we have a diagram,
\begin{center}
\begin{tikzcd}
\cD \arrow[rr, "G"] \arrow[rd, "p"] & & \E \arrow[ld, "q"]
\\
& \cC 
\end{tikzcd}
\end{center}
such that,
\begin{enumerate}
\item $p,q$ are coCartesian
\item $G$ carries coCartesian edges to coCartesian edges
\item each fiber $\cD_C \to \E_C$ for $C \in \cC$ has a left adjoint 
\end{enumerate}
then $G$ has a left adjoint living over $\C$ restricting to left adjoints of the fibers. 
\end{prop}

Now we can define $F : \Fun{}{\Delta1}{\CAlg^\heart} \to \CAlg^{\heart+}$ the left adjoint of $G$ and,
\[ \Omega_{-/\Z} : \CAlg^\heart \xrightarrow{\Delta} \Fun{}{\Delta^1}{\CAlg^\heart} \xrightarrow{F} \CAlg^{\heart +} \]

\section{The Tangent Bundle}

How do we construt $\CAlg^+$ in the $\infty$-setting? 

\begin{theorem}[HA, 7.3.4.14]
For $\EE_{\infty}$-ring $A$ there is a canonical equivalence,
\[ \Sp(\CAlg_{/A}) \cong \Mod_A \]
\end{theorem}

\begin{rmk}
The above map is the analog of $M \mapsto (A \oplus M \to A)$. Indeed, a diagram of this sort can be delooped infinitely many times since,
\begin{center}
\begin{tikzcd}
A \oplus M \pullback \arrow[r] \arrow[d] & A \arrow[d]
\\
A \arrow[r] & A \oplus M[1] 
\end{tikzcd}
\end{center}
The inverse should be given by taking the kernel of the evaluation on $S^0$. From the standard sequence $* \to S^0 \to *$ we see that the extensions we get are always split, there are maps $A \to A \oplus M \to A$ composing to the identity.
\end{rmk}

Idea: take the ``relative stabilization'' of $\ev_1 : \Fun{}{\Delta^1}{\CAlg} \to \CAlg$. 

\begin{defn}
For $C$ a presentable $\infty$-category, define the \textit{tangent bundle} of $\C$,
\[ T_{\C} \subset \Fun{}{\S_*^{\text{fin}}}{\C} \]
sending the full sub of excisive functors (i.e. pushout maps to pullbacks). 
\end{defn}

\begin{prop}
Then $F$-acts: like $\CAlg^{\heart +}$,
\begin{enumerate}
\item there a diagram,
\begin{center}
\begin{tikzcd}
T_{\C} \arrow[rr, "G"] \arrow[rd] & & \Fun{}{\Delta^1}{\C} \arrow[ld, "\ev_1"]
\\
& \C
\end{tikzcd}
\end{center}
\item the fiber of $T_{\C} \to \C$ at $A \in \C$ is $\Sp(\C_{/A})$

\item $T_\C \to \C$ is both Cartesian and coCartesian

\item $G$ sends Cartesian edges to Cartesian edges

\item $\Omega^\infty : \Sp(\C_{/A}) \to \C_{/A}$ has a left adjoint $\Sigma^\infty$.
\end{enumerate}
\end{prop}

Now we can define $F : \Fun{}{\Delta^1}{\C} \to T_{\C}$ and the left adjoint and,
\[ \LL_{(-)} : \C \xrightarrow{\Delta} \Fun{}{\Delta^1}{\C} \xrightarrow{F} T_\C \]

\begin{rmk}
This is absolute: i.e. over the sphere spectrum. 
\end{rmk}

\subsection{The Relative Cotangent Complex}

\begin{defn}
$F : A \to B$ in $\C$ define $\LL_{B/A}$ as the cofiber,
\[ f_! \LL_A \to \LL_B \to \L_{B/A} \]
inside $\Sp(\C_{/B})$.
\end{defn}

\begin{rmk}
Where $T_{\C} \to \C$ is Cartesian so we can lift maps $f : A \to B$ to functors $f_!$. Notice, we did this in the category of spectra (which is a stable $\infty$-category) so that this homotopy fiber automatically gives an ``exact triangle''.
\end{rmk}

This can be upgraded to give $\L_{-/-} : \Fun{}{\Delta^1}{\C} \to T_{\C}$.

\begin{theorem}
For $A \in \C$ the functor,
\[ \LL^{\C_{A/}} : \C_{A/} \to T_{\C_{A/}} \]
can be identified with $B \mapsto \LL_{B/A}$. 
\end{theorem}

\begin{theorem}
$T_{\C_{A/}} \cong \T_{\C} \times_{\C} \C_{A/}$.
\end{theorem}

\begin{rmk}
The idea: $\Sp(\C_{A//B}) \cong \Sp(\C_{/B})$.
\end{rmk}

\subsection{The Cotangent Complex}

\begin{prop}
$\LL_{(-)} : \C \to T_{\C}$ commutes with all small colimits.
\end{prop}

\begin{proof}
It is $F \circ \Delta$ but both preserve small colimits. 
\end{proof}

\begin{rmk}
Colimits in $T_{\C}$ can be computed by,
\begin{enumerate}
\item compute colimit of composition with $T_{\C} \to \C$ (say $X \in \C$)

\item use coCartesian lifts to move diagram to $\Sp(\C_{/X}) = (\T_\C)_X$

\item compute colimits in this fiber. 
\end{enumerate}
\end{rmk}

\begin{prop}
If $A = \dlim A_i$ in $\C$ then $\LL_{A} = \dlim (A_i \to A)_{!} \LL_{A_i}$ where this colimits is computed in $(T_\C)_A$.
\end{prop}

\begin{cor}
$\LL_A = \dlim (A \ot^{\LL}_{A_i} \LL_{A_i})$
\end{cor}

\begin{prop}
If $A = \dlim A_i$ and $B = \dlim_{B_i}$ with maps $A_i \to B_i$ compatible to give $A \to B$. Then,
\[ \L_{B/A} = \dlim (B_i \to B)_! \LL_{B_i / A_i} \]
\end{prop}

\begin{cor}
$\LL_{B/A} = \dlim (B \ot_{B_i}^{\LL} \LL_{B_i/A})$.
\end{cor}

\begin{rmk}
This explains what we were doing before. We defined the right thing on onlynomial algebras and then forced it to commute with sifted colimits.
\end{rmk}

\begin{prop}
If,
\begin{center}
\begin{tikzcd}
A \arrow[r] \arrow[d] & B \arrow[d]
\\
A' \arrow[r] & \pushout B'
\end{tikzcd}
\end{center}
is a pushout diagram. Then,
\[ \LL_{B'/A'} = (B \to B')_{!} \LL_{B/A} \]
\end{prop}

\begin{rmk}
This is actually NOT the cotangent complex we're used to. 
\end{rmk}

\begin{example}
$\LL_{\Z[x]/\Z} \not\cong \ZZ[x]$ there is higher junk.
\end{example}

\begin{rmk}
The right thing is to take $\ZZ \{ x \}$ which is free in the spectral sense. This is the adjoint to the forgetful map. Then,
\[ \LL_{\Z \{ x \}/\Z} \cong \ZZ \{ x \} \]
However, $\pi_0(R \{ x \}) = \pi_0(R[x]) = \pi_0(R)[x]$ so the topological spaces are the same. 
\end{rmk}

\section{Mar. 16 Examples of Ring Spectra}


\subsection{Eilenberg-Maclane spectrum}

If $R$ is a ring then the Eilenberg-Maclane spectrum $HR$ is a ring spectrum. Indeed,
\[ [ \Sigma^\infty, HR] = H^*(X, R) \]
also we see that,
\[ \pi_k((HR)_n \wedge (HR)_m) = 
\begin{cases}
R \ot R & k = m + n
\\
0 & k < m + n
\end{cases} \]
Then by Hurewicz,
\[ H^{n+m}((HR)_n \wedge (HR)_m; R) = \Hom{}{R \ot_\Z R}{R} \]
which contains a distinguished element $\mu : R \ot_\Z R \to R$ defined by the multiplication map. Therefore, we get maps,
\[ (HR)_n \wedge (HR)_m \to (HR)_{n+m} \]
which fit together to give,
\[ HR \wedge HR \to HR \]
and this gives $HR$ the structure of a ring spectum.

\subsection{Bordism}

$MU(n) = \Th(E U(n)) = D(U(n)) / S(U(n))$.
The maps $\CC^n \to \CC^{n+1}$ via $z \mapsto (z,0)$ gives $U(n) \to U(n+1)$ whcih gives a map $\iota : B U(n) \to B U(n+1)$.
\bigskip\\
Then $\iota^* EU(n+1) = EU(n) \oplus \epsilon$. Then,
\[ \Th(\iota^* EU(n+1)) = \Sigma^2 \Th(EU(n)) \]
The ring structure is given by 
DO THIS


\begin{defn}
Stably almost complex manifold is an embedding,
\[ M \embed \RR^N \]
such that $N_{M}$ is equipped with an almost complex structure.
\end{defn}

The normal bundle is then given by classifying map $M \to BU(N-n)$

\end{document}