\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}

\section{del Pezzo Surfaces}

\begin{defn}
A surface is \textit{del Pezzo} if it has cyclic quotient singularities and $-K_X$ is ample (note that $X$ need not be Gorenstein so $K_X$ is just $\Q$-Cartier).  
\end{defn}

\begin{rmk}
We can to classify these up to $qG$-deformations. The idea of a $qG$-deformation is a family of del Pezzo surfaces $X \to S$ such that $\deg(-K_{X_s})^2$ and $h^0(X_s, -K_{X_s})$ are locally constant on the base (the intersection numbers are automatically constant for flat families). 
\end{rmk}

\subsection{Mirror Symmetry for Fanos}

Let $X$ be a smooth Famo and $p_\beta$ is some count of stable maps of class $\beta$ to $X$ though a fixed generic point. More precisesly,
\[ P_\beta = (d_\beta)! \int_{M_{0,1}(X, \beta)} \ev^* [*] \cdot \psi^{d_{\beta} - 2} \]
where $d \beta = - \deg{(K_X \cdot \beta)}$ is an anti-canonical degree. These are stable maps with $f_* [C] = \beta$ where $[C]$ is the fundamental class. 
\bigskip\\
We fit these together into a generating function,
\[ \hat{G}_X(z) := \sum_{\beta \in \mathrm{NE}(X)} P_{\beta} \cdot z^\beta \in \Q[[\mathrm{NE}(X)]] \]
We can replace $z^\beta \mapsto t^{d_{\beta}}$ which gives a power series,
\[ \hat{G}_X(t) \in \Q[[t]] \]
This is one side of the mirror symmetry story. On the other side we have,
\[ f \in \Q[x^{\pm}, y^{\pm}] \]
then consider,
\[ \pi_f = \int_{|z_1| = |z_2| = 1} \frac{\Omega}{1 - t f} = \sum_{d \ge 0} c_0(f^d) t^d \in \Q[[t]] \]
where $c_0(g)$ is the constant coeffiicent as a Laruent polynomial. We say that $f$ is mirror to $X$ if,
\[ \pi_f(t) = \hat{G}_X(t) \]
Note that $f$ is not unique if it exists. 

\subsection{Conjectures}

\begin{defn}
A Fano variety if of class $TG$ if there is a $qG$-deformation to a toric variety.
\end{defn}

\begin{conjecture}
There exists a bijection,
\[ \{ X \text{ Fano and of class } TG \} / \{ \text{qG-defomration} \iff \{ \text{Fano polytopes} \} / \text{mutations} \]
given by $P \mapsto [X_P]$. 
\end{conjecture}

\subsection{Evidence}

Smooth del Pezzos there are $\mathrm{Bl}_{k \text{points}} \P^2$ for $0 \le k \le 8$ and $\P^1 \times \P^1$ then the $qG$-deformations gives 10 families (allthough many of these families have a unique member). 

\begin{thm}
The map $ \{ \text{Fano Poly} \} / \{\text{mutation}\} \to \{ X \text{ Fano TG} \} / \sim$ is well defined.
\end{thm}

\subsection{Gross - Siebert Program}

Let $(X, D)$ be a smooth del Pezzo pair $D$ is an anticanonical divisor (snc and a cycle of lines maybe). The Gross-Siebert program produces an algebra,
\[ A = \bigoplus_{P \in B(\Z)} \theta_p \CC[\mathrm{NE}(X)] \]
where we define,
\[ \theta_p \cdot \theta_q = \sum_{r \in B(\Z)} \alpha_{pqr} \theta_r \]
with $\alpha_{pqr} \in \C[\mathrm{NE}(X)]$ is defined as some Gromov-Witten invariant. Then we get,
\[ Y = \Spec{A} \to \Spec{\CC[\mathrm{NE}(X)]} \]

\end{document}

