\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}

\section{Motivation}

\renewcommand{\GL}{\mathrm{GL}}
\renewcommand{\PGL}{\mathrm{PGL}}

Let $X$ be a normal (quasi-projective) variety over a field $k$. Then,
\[ H^1(X, \Gm) = \{ \lambda_{ij} \in \Gm(U_{ij}) \} / \{ \delta_i \in \Gm(U_i) \}  \]
is the group of line bundles. 

\begin{rmk}
For (quasi-projective, I think) $X$ the Cech and etale cohmology groups agree. Therefore, when we write $H^i(X,-)$ we are going to mean $\check{H}^i(X,-)$ on the \etale site. 
\end{rmk}

Then,
\[ H^2(X, \Gm) = \{ \text{azumaya algebras} \} / \text{morita equivalence} \]
where Azumaya algebras are equivalent to $\mathrm{PGL}_r$-bundles on $X$. These also classify $\Gm$-gerbes on $X$ where a $\Gm$-gerbe is a stack locally isomorphic to $X \times B \Gm$. This alows us to write double intersection data in terms of single intersection data. 
\bigskip\\
Then the transition functions,
\[ U \times B \Gm |_{U \cap V} \xrightarrow{\varphi_{U \cap V}} V \times B \Gm |_{U \cap V} \]
This is given by a map $U \cap V \to B \Gm$ and therefore by a line bundle $\L_{U \cap V} \in \Pic{U \cap V}$. 
Therefore we have $\L_{ij}$ on each $U_{ij}$ and then there is the data of an isomorphism,
\[ \varphi : \L_{ij} \ot \L_{jk} \ot \L_{ik}^{-1} \iso \struct{U_{ijk}} \]
and therefore we get a $\Gm(U_{ijk})$-torsor of choices of $\varphi$. This defines a class $[\alpha] \in H^2(X, \Gm)$. Then we could say that,
\[ H^2(X, \Gm) = H^1(X, \Pic{X}) \]
where $\Pic{X}$ is the Picard stack. 

\begin{center}
\begin{tikzcd}
0 \arrow[r] & \Gm \arrow[r] & \GL_r \arrow[r] & \PGL_r \arrow[r] & 0
\end{tikzcd}
\end{center}
Therefore we get a map $H^1(X, \PGL_r) \to H^2(X, \Gm)$ and as we vary over $r$ these are jointly surjective (HARD). We want another perspective on Mortia equivalence which is somehow the same as taking the cokernel $H^1(X, \GL_r) \to H^1(X, \PGL_r)$. 

\begin{defn}
Morita equivalence is $A \sim B$ if their category of modules are equivalent (probably in a was preserving the underlying abelian sheaf). 
\end{defn}

\begin{thm}[Krashen-T]
Let $X$ be a smooth projective variety over $k$. Then,
\[ H^3(X, \Gm) \iso \{ 2\text{-azumaya algebras} \} / \text{morita equivalence} \]
\end{thm}

\section{Detour into dgLand}

\begin{defn}
A dg-algera is a differential graded algebra and a dg-algebra is a graded module over this dg-algebra. 
\end{defn}

\newcommand{\Br}[1]{\mathrm{Br}\left( #1 \right)}

\begin{rmk}
We want a modoidal cateogory in which $\Br{X}$ represents the units. 
\end{rmk}

\begin{example}
$H^1(X, \Gm) = \Coh{X}^\times$
\end{example}

\begin{prop}
$\Br{X} = (\struct{X}\text{-de-CAT}/\sim_{\text{mor}})^\times$.
\end{prop}

\begin{defn}
An $A$-dg-cat is a cateogry enriched in $A$-dg-modules.
\end{defn}

\begin{thm}
There exists a well-defined cateory $C$ consisting of $\struct{X}$-dg-cat up to morita equivalence and a map,
\[ \varphi : H^2(X, \Gm) \embed C \]
whose image is precise the invertables of $C$ under the $\ot$-structure. We define,
\[ \varphi(A) = *_A \]
the category with one object and $A$ of morphisms. Then $\Br{X} \acts C$ by automorphisms.
\end{thm}

\begin{defn}
A $2$-azumaya algebra $\cA$ over $X$ is a 2-stack of dg-categories such that,
\begin{enumerate}
\item $\cA|_U \cong C|_U$ for a cover $U \to X$
\item $\Hom{}{\cA}{\cA} \cong C$ in $C$.
\end{enumerate}
\end{defn}

\begin{prop}
$H^3(X, \Gm) \cong \{ 2 \text{-azumaya algebra} \}$
\end{prop}

\begin{proof}
$\cA$ is given by a class in $\Br{U}$ over each  double intersection. Define the cover to go from,
\[ H^1(X, \Br{X}) \to H^3(X, \Gm) \]
\end{proof}

\end{document}
