\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\usepackage{import}
\import{../}{AlgGeoCommands}

\begin{document}
\section{Complex Singularities on Hypersurfaces (Milnor, Brieskorn)}

Let $A \cong \CC \{ z_1, \dots, z_n \} / (y^2 - x^n)$ where $\CC \{ x_1, \dots, z_n \}$ is the algebra of convergent power series. 

\begin{defn}
A \textit{germ} is an element of the opposite category of these algebras.
\end{defn}

\begin{defn}
A \textit{deformation} of a germ $X_0$ is a flat mop of germs $f : X \to S$ where $S$ has a distinguished point $0 \in S$ sauch that,
\begin{center}
\begin{tikzcd}
X_0 \arrow[d] \arrow[r] & X \arrow[d]
\\
* \arrow[r] & S
\end{tikzcd}
\end{center}
(is Cartesian probably?)
There is an equivalence relation under,
\begin{center}
\begin{tikzcd}
X' \arrow[d] \arrow[r] & X \arrow[d]
\\
S' \arrow[r] & S
\end{tikzcd}
\end{center}
\end{defn}

\begin{example}
Milnor considered deformations of the form,
\begin{center}
\begin{tikzcd}
\CC \{ x, y \} \arrow[r=from] & \frac{\CC \{ x, y, s \}}{(y^2 - x^n + s)}
\\
\CC \arrow[u] \arrow[r=from] & \CC \{ s \} \arrow[u]
\end{tikzcd}
\end{center}
(remember the arrows go the other way for germs).
\end{example}

\subsection{The Topology}

Let $f(z_0, z_1, \dots, z_n)$ be a nonconst polynomial in $n + 1 \ge 2$ complex vars. Then,
\[ V = \{ z \mid f(z) = 0 \} \]
is a complex hypersurface of dimension $n$. Consider,
\[ V \cap S_\epsilon(z^0) = K \]
where $z^\bullet$ is a singular point and $S_\epsilon(z^0)$ is the $(2n+1)$-sphere of radius $\epsilon > 0$ about $z^0$ in the ambiant $\CC^n$-space. 
\bigskip\\
If $z^0$ is regular point, $V$ smooth dim $2n$ then $K$ is a smooth $(2n - 1)$-dim manifold diffeomorphic to $(2n - 1)$-sphere. Then $K \embed S_\epsilon$ is a knotted sphere.

\begin{example}
If $f(z_1, z_2) = z_1^p  + z_2^q$ with $(p,q) = 1$ and $p,q \ge 2$ so there is a singularity at the origin.
\end{example} 

\begin{prop}[Brauner]
$f^{-1}(0) \cap S_\epsilon$ is a $(p,q)$-torus knot.
\end{prop}

\begin{rmk}
We want to consider cases where $K$ is homeomorphic to $S^{2n-1}$. However, it is possible that $K$ has a nonstandard smooth structure from the induced submanifold structure!
\end{rmk}
\noindent
Introduce a fibration for describing $K \embed S_\epsilon$.

\begin{thm}[Milnor]
If $z^0 \in V$ and $\epsilon > 0$ sufficiently small and $S_\epsilon(z^0)$ is the sphere of radius $\epsilon$ at $z^0$. Then let $\phi : S_\epsilon \setminus K \to S^1$ defined by,
\[ \phi(z) = \frac{f(z)}{|f(z)|} \] 
viewing $S^1$ as the complex unit circle. Then $\phi$ forms a smooth fiber bundle with each fiber $F_{\theta} = \phi^{-1}(e^{i \theta}) \subset S_\epsilon \setminus K$ is a paralllelizable $2n$-dimensional manifold.
\bigskip\\
Furthermore, if $z^0$ is an isolated singularity then $F_\theta$ is homotopy equivalent to $S^n \vee \cdots \vee S^n$.
\end{thm}

\begin{rmk}
The proof of this theorem goes through Morse theory.
\end{rmk}

\begin{rmk}
Is $K = f^{-1}(0) \cap S_\epsilon$ a topological sphere? Any two $n$-dimensional homology classes $\alpha, \beta$ of $F_{\theta}$ have a geometric intersection number $s(\alpha, \beta)$
\end{rmk}

\begin{lemma}
$K$ is a $\Z$-homology sphere iff $s : H_n(F_\theta) \ot H_n(F_\theta) \to \Z$ has determinant $\pm 1$. 
\end{lemma}

\begin{rmk}
Given a fiber bundle $\phi : E \to S^1$ there is an action of $1 \in \pi(S^1)$ on homology of the fiber. It is given by an automorphism $h_* : H_*(F_\theta) \to H_*(F_\theta)$. We call $h$ the characteristic homeomorphism of $F_1 = \phi^{-1}(1)$. Define,
\[ \Delta(t) = \det{(t I_* - h_* | H_*(F_\theta))} \] 
is related to the alexander polynomial of $K$. 
\end{rmk}

\begin{thm}
If $n \neq 2$ then $K$ is a topological sphere if and only if $\Delta(1) = \det{(I_* - h_*)} = \pm 1$. 
\end{thm}
 
\section{Brieskorn Varieties}

For $a_1, \dots, a_{n+1} \ge 2$ coprime integers then let,
\[ f(z_1, \dots, z_n) = (z_1)^{a_1} + \cdots + (z_{n+1})^{a_{n+1}} \]
Then let $V = f^{-1}(0)$ be the hypersurface defined by $f$. The origin is the unique singular point of $V$. Then let,
\[ K = f^{-1}(0) \cap S_\epsilon \]
is smooth of dimension $2n - 1$. Consider fibration,
\[ \phi : S_\epsilon \setminus K \to S^1 \]
the fibers are $F_\theta$.  
 
\begin{thm}[Brieskorn-Pham]
$H_n(F_\theta)$ is free of rank,
\[M = (a_1 - 1) \cdots (a_{n+1} - 1)\]
and the roots of $\Delta(t)$ are exactly the set of all products,
\[ \omega_1 \cdots \omega_{n+1} \]
where $\omega_i$ range over the $a_i^{\text{th}}$-roots of unity besides $1$ (of which there are $a_i - 1$) for each $i$. Thus,
\[ \Delta(t) = \prod_{\omega} (t - \omega_1 \cdots \omega_{n+1}) \]
\end{thm} 

\begin{example}
For $a_1 = \cdots = a_n = 2$ and $a_{n+1} = 3$ we call this the ``generalized trefoil'' (because $a_1 = 2$ and $a_2 = 3$ gives exactly a trefoil knot in $S_3$). Then,
\[ \omega_1 = \cdots \omega_n = -1 \quad \text{ and } \quad \omega_{n+1} = \frac{-1 \pm i \sqrt{3}}{2} \]
Therefore,
\[ \Delta(t) = \left( t - (-1)^n \zeta_3 \right) \left( t - (-1)^n \bar{\zeta_3} \right) = t^2 + (-1)^n t + 1 \]
Therefore $K$ is a topological sphere for dimension $1,5,9,13, \dots$ and for dimension $9$ you get Kervera's exotic sphere. 
\end{example}
 
\end{document}

