\documentclass[12pt]{article}
\usepackage{import}
\import{./}{LogicCommands}

\begin{document}

\newcommand{\rec}{\mathrm{rec}}
\newcommand{\ind}{\mathrm{ind}}
\renewcommand{\succ}{\mathrm{succ}}
\newcommand{\pr}{\mathrm{pr}}

\newcommand{\cU}{\mathcal{U}}

\section{Introduction}

The point of homotopy type theory is to create a logical system in which isomorphism and equality are ``the same''. Of course, to say this we must furthermore ask what kind of ``the same'' is this? Should we say that isomorphism and equality are equal or are they isomorphic and what does that mean? Our theory will in fact satisfy the \textit{univalence axiom}: the natural map
\[ \mathrm{idtoeqv} : (A =_{\cU} B) \to (A \simeq B) \]
is an equivalence. We want to understand what this means.

The total loop space:
\[ \Sigma_{x \in A} (x =_A x) \]
The total path space:
\[ \Sigma_{x,y \in A} (x =_A y) \]

\section{Chapter 1}

\subsection{Exercises}

\subsubsection{Exercise 1.9}

\begin{exercise}
Define the type family $\rm{Fin} : \N \to \U$ and dependent function $\rm{fmax} : \prod\limits_{n : \N} \rm{Fin}(\succ(n))$.
\end{exercise}

We use the recursive type constructor,
\[ \rm{Fin} = \rec_{\N}(\U, \bf{0}, \lambda n. \lambda A. (A + \bf{1})) \]
This satisfies,
\[ \rm{Fin}(0) :\equiv \bf{0} \quad \rm{Fin}(\succ(n)) :\equiv \rm{Fin}(n) + \bf{1} \] 
then the max function also has an inductive construction using the type family $\rm{Fin}$,
\[ \rm{fmax} = \ind_{\N}(\rm{Fin} \circ \succ, \star, c_s) \]
where,
\[ c_s : \prod_{n : \N} \rm{Fin}(\succ(n)) \to \rm{Fin}(\succ(\succ(n))) \]
is the function,
\[ c_s(n, q) :\equiv \rm{inr}(\star) \]
Which satisfies the properties,
\[ \rm{fmax}(0) \equiv \star : \bf{1} \quad \rm{fmax}(\succ(n)) \equiv \rm{inr}(\star) : \rm{Fin}(\succ(n)) + \bf{1} \]

\subsubsection{Exercise 1.10}

\newcommand{\ack}{\mathrm{ack}}

\begin{exercise}
Show that the Ackermann function $\ack : \N \to \N \to \N$ is definable using only $\rec_{\N}$ satisfying the following equations:
\begin{align*}
\ack(0,n) & \equiv \succ(n)
\\
\ack(\succ(m), 0) & \equiv \ack(m, 1)
\\
\ack(\succ(m), \succ(n)) & \equiv \ack(m, \ack(\succ(m), n))
\end{align*}
\end{exercise}

We define the following,
\[ \ack :\equiv \rec_{\N}(\N \to \N, \succ, \lambda (m : \N) . \lambda (g : \N \to \N) . \lambda (n : \N) . c_s(n, g, m)) \]
where,
\[ c_s :\equiv \rec_{\N}((\N \to \N) \to (\N \to \N), \lambda (g : \N \to \N) . \lambda (m : \N) . g(1), u) \]
where,
\[ u :\equiv \lambda (n : \N) . \lambda (c : (\N \to \N) \to (\N \to \N)) . \lambda (g : \N \to \N) . \lambda (m : \N) . g (c(g,m)) \]
Then we have the following,
\[ c_s(0) \equiv \lambda (g : \N \to \N) . \lambda (m : \N) . g(1) \]
and 
\[ c_s(\succ(n)) \equiv u(n, c_s(n)) \equiv \lambda (g : \N \to \N) . \lambda (m : \N) . g(c_s(n, g, m)) \]
Therefore,
\[ \ack(0) \equiv \succ \quad \text{ meaning } \ack(0, n) \equiv \succ(n) \]
and also,
\[ \ack(\succ(m)) \equiv [\lambda (m : \N) . \lambda (g : \N \to \N) . \lambda (n : \N) . c_s(n, g, m)](m, \ack(m)) \equiv \lambda (n : \N) . c_s(n, \ack(m), m) \]
This means that,
\[ \ack(\succ(m), n) \equiv c_s(n, \ack(m), m) \]
so in particular,
\[ \ack(\succ(m), 0) \equiv c_s(0, \ack(m), m) \equiv \ack(m, 1) \]
and also,
\[ \ack(\succ(m), \succ(n)) \equiv c_s(\succ(n), \ack(m), m) \equiv \ack(m, c_s(n, \ack(m), m)) \equiv \ack(m, \ack(\succ(m), n)) \]


\subsubsection{Exercise 1.11}

\begin{exercise}
Show that for any type $A$ we have $\neg \neg \neg A \to \neg A$. 
\end{exercise}

We need to show that the type $(((A \to \bf{0}) \to \bf{0}) \to \bf{0}) \to (A \to \bf{0})$ is inhabited. Indeed consider,
\[ \lambda (f : \neg \neg \neg A) . \lambda (a : A) . f( \lambda (g : \neg A) . g(a) ) \]

\subsubsection{Exercise 1.12}

\begin{exercise}
Using the propositions as types interpretation, derive the following tautologies,
\begin{enumerate}
\item If $A$ then (if $B$ then $A$).
\item If $A$ then not (not $A$).
\item If (not $A$ or not $B$) then not ($A$ and $B$).
\end{enumerate}
\end{exercise}

\begin{enumerate}
\item $(\lambda (a : A). \lambda (b : B). a) : (A \to B \to A)$
\item $(\lambda (a : A) . \lambda (p : \neg A) . p(a)) : (A \to (A \to \bf{0}) \to \bf{0})$
\item $\rec_{\neg A + \neg B}(\neg (A \times B), [\lambda (p : \neg A) . \lambda (f : A \times B) . p \circ \pr_1(f)], [\lambda (p : \neg B) . \lambda (f : A \times B) . p \circ \pr_2(f)]) : (\neg A + \neg B) \to \neg (A \times B)$
\end{enumerate}

\subsubsection{Exercise 1.15}

\begin{exercise}
Show that the indiscernibility of identicals follows from path induction.
\end{exercise}

We want to show show that for any family of types $C : A \to \U$ there is,
\[ f : \prod_{x,y : A} \prod_{p : x =_A y} C(x) \to C(y) \]
such that,
\[ f(x, x, \refl_x) :\equiv \id_{C(x)} \]
We apply path induction to the family of types,
\[ D(x,y,p) : \equiv C(x) \to C(y) \]
and our base case is,
\[ \prod_{x : A} D(x,x,\refl_x) \equiv \prod_{x : A} C(x) \to C(x) \]
which is inhabited by $\id_C$. Then we set,
\[ f :\equiv \ind_{=_A}(D, \id_C) \]
which satisfies,
\[ f(x,x,\refl_x) :\equiv \id_{C(x)} \]

\section{4 Equivalences}

\subsubsection{Exercise 4.6}

\newcommand{\qinv}{\mathrm{quiv}}

\begin{exercise}
For $A, B : \cU$ define
\[ \mathrm{idtoqinv}_{A,B} : (A =_{\cU} B) \to \sum_{f : A \to B} \qinv(f) \] 
by path induction. Explicitly, consider
\[ C : \prod_{A,B \in \cU} A =_{\cU} B \to \cU \]
defined by 
\[ C(A,B,p) :\equiv \sum_{f : A \to B} \qinv(f) \]
and notice that we have
\[ c : \prod_{A : \cU} C(A, A, \refl_A) \]
defined by,
\[ c(A) = (\id_A, \id_A) \]
therefore, there is an element,
\[ \mathrm{idtoqinv} : \prod_{A, B : \cU} \prod_{p : A =_{\cU} B} \sum_{f : A \to B} \qinv(f) \]
which is the same as an a term
\[ \mathrm{idtoqinv} : \prod_{A, B : \cU} (A =_{\cU} B) \to \sum_{f : A \to B} \qinv(f) \]

Let \textbf{qinv-univalence} denote the modified form of the univalence axiom that asserts that $\mathrm{idtoqinv}$ has a quasi-inverse.

\begin{enumerate}
\item Show that \textbf{qinv-univalence} suffices in the proof of function extension in \S 4.9.
\item Show that \textbf{qinv-univalence} suffices to prove Theorem 4.1.3.
\item Show that \textbf{qinv-univalence} is inconsistent.
\end{enumerate}
\end{exercise}

\begin{enumerate}
\item 
\item 
\item \chref{https://groups.google.com/g/homotopytypetheory/c/EXWVbQNRAdE/m/8g6Xx7aLQeoJ}{look here}.
\end{enumerate}


\section{Examples of Using Univalence}

\begin{exercise} 17.1(a) of \chref{https://arxiv.org/pdf/2212.11082.pdf}{this book}
Show that the type
\[ C :\equiv \sum_{A : \cU} \text{isContr}(A) \]
is contractible.
\end{exercise}

It suffices to show that $C$ is inhabited and for all $A, B : C$ exhibit an element of type $A =_C B$. First note that $1 : C$ or more formally $1$ along with the inductive proof of contractibility. Then for $(A, t_A), (B, t_B) : C$ we need to exhibt elements $p : A =_{\cU} B$ and $\gamma : (p_*(t_A) =_{\text{isContr}(B)} t_B)$. However, $\text{isContr}(B)$ is a mere proposition so the second is free given the first. However, we are given $t_A : \text{isContr}(A)$ and $t_B : \text{isContr}(B)$ so there are elements of $A \simeq 1$ and $B \simeq 1$ which compose to give $A \simeq B$ and hence by the inverse univalence map $A =_{\cU} B$.
\end{document}
