\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\urlstyle{same}
\usepackage{import}
\import{../}{AlgGeoCommands}


\begin{document}


\section{Cohomological Non Abelian Theorems in Char $p$}

\subsection{The Situation over $\CC$}

We have three cohomology spaces,
\[ \M_{\text{Dol}}(C) \sim \M_{\dR}(C) \sim \M_{B}(C) \]
the first is the stack of Higgs bundles $(E, \phi)$ with $\phi : E \to E \ot \Omega^1$ which is $\struct{}$-linear. The second is the space of flat connections and the third is the space of representations of $\pi_1(C)$. The first equivalence is by Hitchen the second is by Riemann-Hilbert.

\begin{enumerate}
\item $h : \M_{\text{Dol}}(C) \to A(C) = \bigoplus_{i = 1}^r H^0(C, \omega_C^{\ot r})$
sending $(E, \phi) \mapsto \mathrm{char}(\phi)$ the characteristic polynomial. This is the Hitchin morphism.

\item $\M_{\text{Hod}}(C)$ is the space of $t$-connections,
\[ \nabla_t(f e) = t \d{f} + f \nabla_t(e) \]
There is a map $\M_{\text{Hod}}(C) \to \A^1$ given by $t$ and the $1$-fiber is $\M_{\dR}$ and the $0$-fiber is $\M_{\text{Dol}}$.
\end{enumerate} 

\subsection{Characteristic $p$}

\newcommand{\Frob}{\mathrm{Frob}}

Let $k = \bar{k}$ and $\ch{k} = p$. Let $\partial \in \mathrm{Der}(C/k)$ then $\partial^p = \partial \circ \cdots \circ \partial$ is a derivation. Then the $p$-curvature of $\nabla_t$ is,
\[ \Psi(\nabla_t)(\partial) := \nabla_t(\partial)^p - t^{p-1} \nabla_t(\partial^p) \in \End[\struct{C}]{E} \]
is $\struct{C}$-linear. However,
\[ \Psi(\nabla_t)(f \partial) = f^p \Psi(\nabla_t)(\partial) \]
and therefore defines a map,
\[ \Psi(\nabla_t) : TC \to \Frob_* \End[\struct{C}]{E} \]

\begin{rmk}
The map $\Frob : C \to C^{(1)}$ is the relative Frobenius over the field $k$.
\end{rmk}

Therefore, $\Phi(\nabla_t) : E \to E \ot \omega_C^{\ot p}$ is a $\omega_C^{\ot p}$-Higgs bundle. Then,
\begin{center}
\begin{tikzcd}
\M_{\text{Hod}}(C) \arrow[r, "\Psi"] \arrow[rrd, "h_{\text{Hod}}"] & \M_{\text{Dol}}(C, \omega_C^{\ot p}) \arrow[r] & A(C, \omega_C^{\ot p}) \times \A^1
\\
& & A(C, \omega_{C^{(1)}}) \times \A^1
\end{tikzcd}
\end{center}
There is a unique map $h_{\text{Hod}}$ making the diagram commute. Then for $(r, d) = 1$ (rank $r$ and degree $d$) consider the diagram,
\begin{center}
\begin{tikzcd}
\M_{\text{Dol}}(C) \arrow[r] & \M_{\text{Hod}}(C) \arrow[d, "h_{\text{Hod}}"] & \M_{\dR}(C) \arrow[d, "h_{\dR}"]
\\
A(C^{(1)}) \arrow[r, "0"] & A(C^{(1)}) \times \A^1 \arrow[d] & A(C^{(1)})
\\
& \A^1
\end{tikzcd}
\end{center}

\begin{theorem}
$H^*(\M_{\text{Dol}}(C)) \leftarrow H^*(\M_{\text{Hod}}(C)) \to H^*(\M_{\dR}(C)) \]
are isomorphisms.
\end{theorem}

\begin{theorem}
For the diagram,
\begin{center}
\begin{tikzcd}
\M_{\text{Dol}}(C^{(1)}) \arrow[rd, "h"] & & \M_{\dR}(C) \arrow[ld, "h_{\dR}"]
\\
& A(C^{(1)}) 
\end{tikzcd}
\end{center}
Then we have,
\[ h_* \mathrm{IC}_{\M_{\text{Dol}}(C^{(1)}, d)} \iso (h_{\dR})_* \mathrm{IC}_{\M_{\dR}(C, dp)} \]
\end{theorem}



\end{document}
