\documentclass[12pt]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\urlstyle{same}
\usepackage{import}
\import{../}{AlgGeoCommands}

\newcommand{\Qbar}{\overline{\Q}}


\begin{document}
\section{Motivation}

\begin{theorem}
$X$ is smooth quasi-projective over $\CC$ there exists a $\CC$-local system $L_{\CC}$ of rank $r$ such that for all primes $\ell$ there is $L_{\ell}$ an $\ell$-adic local system of rank $r$ which is $\Qbar_\ell$-irreducible and $\det{L_{\ell}} \cong \L$ and monodromy at $\infty$ up to ... 
\end{theorem}

Uses tools of companions and hust Langlands. 

\begin{rmk}
Let $\pi$ be the finitely presented group this gives an obstruction to $\pi = \pi_1(X(\CC))$ of a smooth quasi-projective variety $X$. 
\end{rmk}

\begin{defn}
The character variety $\Ch(\pi, r)$ is \textit{weakly-integral} if,
\begin{enumerate}
\item there is an irreducible $\rho : \pi \to \GL_r(\CC)$ 
\item then for any $\ell$ there is a $\Qbar_\ell$-irred representation $\rho_{\ell} : \widehat{\pi} \to \GL_r(\Z_\ell)$ such that $\det{\rho_{\ell}} = \rho_{\det}$.
\end{enumerate}
\end{defn}

\begin{example}
Let $\pi = \SL(2, \Z)$. There is an irreducible $\CC$-rep but no integral rep at $\ell = 2$.
\end{example}

\begin{theorem}
Let $Y, X$ be smooth projective over $\CC$ and $f : Y \to X$ and $L_{\CC}$ semisimple local system on $X$ then $f^* L_{\CC}$ is semisimple. 
\end{theorem}

\begin{rmk}
This is proved using harmonic geometry. We can prove it again using arithmetic geometry. 
\end{rmk}

\begin{rmk}
Since $\pi_1(X(\CC))$ is finitely generated, there is a finite type $\Z$-algebra $A \subset \CC$ such that,
\begin{center}
\begin{tikzcd}
\pi_1(X(\CC)) \arrow[rd] \arrow[r] & \GL_r(\CC)
\\
& \GL_r(A) \arrow[u]
\end{tikzcd}
\end{center}
There exists some $\ell$ so we can map $A \to \Z_\ell$. This will not give all primes however. 
\end{rmk}

\subsection{Another Formulation}

\newcommand{\irred}{\mathrm{irred}}

Consider the moduli space $M_B(X, r, \L, T_i)$ where $\L$ is the determinant and $T_i$ are the monodromy at $\infty$. This is defines over some number field $K \supset \Q$. In fact it is defined,
\[ M^{\irred}_B(X, r, \L, T_i) \to \Spec{\struct{K}} \]
Then $\L_{\CC}$ maps to $\Spec{\CC} \to \Spec{\struct{K}}$. Then the map is dominant so there are at most finitely many primes not in the image. Another version of the theorem is that the map is surjective. 

\begin{rmk}
Irreducible means a representation $\rho : \pi \to \GL_r(A)$ then must be irreducible at each localization (and completion?).
\end{rmk}

\begin{rmk}
Given a point over characteristic $\ell$ such that it is the mod $\ell$-reduction of the DVR then I get an $\ell$-adic local system. Given $z \in M_B$ closed with $\kappa(z) = \FF_{\ell^n}$. Assume there is an $R$ finite over $W"(\FF_{\ell^n})$ with residue field $\FF_{\ell^n}$ with $\Spec{R} \to M_B$ specializing to $z$. Then we get a representation $L_R$ topological local system,
\[ \pi_1(X(\CC)) \to \GL_r(R) \]
but $R$ is profinite so we get a factorization through the completetion. 
\end{rmk}

Sketch of the proof: $(M_B)_{\red} \to \Spec{\struct{K}}$ is generically smooth. Therefore, there is an open $U \subset M_B$ where the reduced map is smooth. Choose some closed point $z \in U$. There is a map $D \to \widehat{M_B}_z$ where $D$ is Mazur's deformation space. Its points are $\Z_\ell$-representations which lift $z$. 

\end{document}
